---
title: "Triangulation Error analyses with razimuth"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: "Matteo Rizzuto"
output:
  rmdformats::html_clean:
    self_contained: false
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
    fig_width: 8
    fig_height: 6
    df_print: paged
  pdf_document:
    citation_package: biblatex
    dev: pdf
    fig_caption: true
    fig_crop: TRUE
    highlight: tango
    keep_tex: true
    latex_engine: pdflatex
    toc: true
    toc_depth: 2
    number_sections: false
    df_print: kable    
fontsize: 11pt
geometry: margin=1in
documentclass: article    
bibliography: ../Manuscripts/Rizzuto_etal_StoichHomeRanges.bib
csl: ../Manuscripts/ecology.csl
editor_options: 
  chunk_output_type: inline
---

Here, we investigate the average error in azimuthal data collection for 
two of our observers involved in the telemetry sampling of our snowshoe hares.
We use package `razimuth` to estimate the location of test collars and then
measure the distance between the estimated and true locations using function 
`st_distance` from the `sf` package.

## Rationale

In 2017, a single observer performed all triangulations on the four 
radio-collared snowshoe hares active on our trapping grid. In 2018 and 2019, due
to an increase in both the number of collared hares active on the grid and in 
the workforce available, we had two or three observers simultaneously collecting 
azimuths on each collar. This approach allowed for quicker azimuthal sampling 
for each triangulation bout and also for improved accuracy.

Here, we report the data and code used to estimate the accuracy of our lone 
observer in 2017 (MR) and of one of the observers in 2018 (Mr. Benjamin 
Stratton). During the lead-up to the 2017 and 2018 telemetry sampling seasons, 
we conducted 6 days of error reduction exercises with MR in 2017, and 7 days of 
error reduction exercises with BS in 2018. During each error reduction session, 
the observer would attempt to locate a variable number of collars (n=1-7) 
hidden in advance by a collaborator. In 2017, these exercises took place on the 
trapping grid itself, alongside other sampling activities. In 2018, exercises 
took place in Pippy Park, a large natural area in St. John’s, NL, whose 
vegetation and topography closely resemble the grid itself.

### Data Loading and Wrangling

We begin by loading the error reduction exercises data, checking the structure
of each file, and removing NAs.

```{r error-data-load, echo=TRUE, tidy=TRUE}
# load the error trials data
trialData_2017 <- read.csv("../Data/MR_ErrorReduction.csv")
trialData_2018 <- read.csv("../Data/BS_ErrorReduction.csv")

# remove azimuthal NAs
trialData_2017 <- drop_na(trialData_2017, Azimuth)
trialData_2018 <- drop_na(trialData_2018, Azimuth)

# check structure pre-merge
head(trialData_2017)
head(trialData_2018)

# remove unnecessary columns
trialData_2018 <- trialData_2018[, -1]
# head(trialData_2018)
```

We are going to reproject these data to an up to date datum.

```{r error-data-crs-conversion, echo=TRUE, tidy=TRUE}
# convert all of them to meters
 
trialData_2017 <- drop_na(trialData_2017, Easting)
coordinates(trialData_2017) <- c("Easting", "Northing")
proj4string(trialData_2017) <- CRS("+init=epsg:32622")

trialData_2017 <- spTransform(trialData_2017, CRS("+proj=tmerc +lat_0=0 +lon_0=-61.5 +k=0.9999 +x_0=304800 +y_0=0 +ellps=GRS80 +units=m +no_defs"))
trialData_2017 <- as.data.frame(trialData_2017)
trialData_2017$UTMZone <- as.integer(22)

trialData_2018 <- drop_na(trialData_2018, Easting)
coordinates(trialData_2018) <- c("Easting", "Northing")
proj4string(trialData_2018) <- CRS("+init=epsg:32622")

trialData_2018 <- spTransform(trialData_2018, CRS("+proj=tmerc +lat_0=0 +lon_0=-61.5 +k=0.9999 +x_0=304800 +y_0=0 +ellps=GRS80 +units=m +no_defs"))
trialData_2018 <- as.data.frame(trialData_2018)
trialData_2018$UTMZone <- as.integer(22)
```

`razimuth` requires a column containing the maximum distance between a 
transmitter and a receiver. In 2017, as all trials took place on the snowshoe 
hare live trapping grid but not beyond it, we estimate the maximum distance `r` 
to be 500 m. In 2018, when the trials took place in the Pippy Park natural area 
in St. John's, NL, we estimate `r` to be 750 m. The code below adds the column 
`prior_r` that stores this information to the two error reduction datasets.

```{r error-trials-max-dist, echo=TRUE,tidy=TRUE}
# add column of prior_r. This is the maximum distance (m) between observer and 
# transmitter prior to taking the azimuth. If this was not obtained during data 
# collection, still need to have an upper bound for each azimuth BL grid is 500 
# m wide and test collars were not placed outside of it. So max distance away 
# would be approximately 500 m. Setting this for every row in trialData_2017.

trialData_2017 <- trialData_2017 %>%
  add_column(prior_r = 500)

# In Pippy Park, St. John's NL, trials were at times done from one side of Long 
# Pond to the opposite side, or from the trail leading to the Mt Scio Hill Top. 
# This distance can be around 750 m, so we will set 750 m as our maximum 
# distance for the trials run in 2018.

trialData_2018 <- trialData_2018 %>%
  add_column(prior_r = 750)
```

Now, let's join the two error trial datasets into a new object called `trialData`.

```{r dataset-join, echo=TRUE, tidy=TRUE}
# check a join could work
dplyr::anti_join(trialData_2017, trialData_2018)

# join the two datasets and remove unused levels
trialData <- full_join(trialData_2017, trialData_2018) 
trialData <- droplevels(trialData)

trialData
```

We will now assign a unique group identifier (GID) to each set of triangulations,
that is, the group of azimuths collected when triangulating a given test collar
on a given day. To do this, we will first create a new column, `ID`, that 
uniquely identifies collars across years: this is required as some test collars
were used in multiple years. We will also break down the column `Date` in its
individual components `Year`, `Month`, `Day`. After these two changes to the 
dataset, we will use a loop with nested `if` conditions to assign the GID. 
Finally we will store the new dataset in an object called `erData`.

```{r error-gid-assignement, echo=TRUE, tidy=TRUE}
# break down "Date" column to its individual components but keep it in the dataset
# then create a new column to uniquely identify collars between years
trialData <- trialData %>% 
  separate(., "Date", c("Year", "Month", "Day"), sep = "-", remove = FALSE) %>% 
  unite(., ID, c("Frequency", "Year"), sep = "_", remove = FALSE)  

# isolate the IDs of each data entry, i.e. its unique Frequency
IDs <- trialData$ID 

# extract unique ID values, this vector will be used multiple time to index 
# loops
UniqIDs <- unique(IDs)

# create column names for new df
OutputFields <- c(paste(colnames(trialData)), "GID") 

# add GID column to original data
trialData$GID <- NA    
trialData$GID <- as.factor(trialData$GID)

# create new df, name stands for "error reduction Data"
erData <- trialData[FALSE,] 

# remove useless GID column from original dataset
trialData$GID <- NULL 

# The following loop scans the data for groups of azimuths 
# obtained for each collar on each day of triangulation, and assigns a GID 
# based on the date of collection.

for (i in 1:length(UniqIDs)){
  # first, create a temporary dataset to host each Frequency's data in turn
  TmpInds <- which(IDs == UniqIDs[i]) 
  TmpData <- trialData[TmpInds,]   
  # assign a starting GID
  TmpData[1, "GID"] <- 1 
  for (j in 1:(nrow(TmpData) - 1)){
    # if the Date does not change, we want the GID to stay the same
      if (TmpData[j + 1, "Date"] == TmpData[j, "Date"]){
        TmpData[j + 1, "GID"] <- TmpData[j, "GID"]
      }
      else {
        # if the Date changes, we want the GID to increase accordingly
        TmpData[j + 1, "GID"] <- TmpData[j, "GID"] + 1
      }
  }
  # browser()
  # bind each temp dataset into a new one
  erData <- rbind(erData, TmpData) 
}

erData$GID <- as.factor(erData$GID)
erData$Time <- as.numeric(erData$Time)
```

`razimuth` requires the information on the day and time when an azimuth was
collected to be stored in a column with format `YYYY-MM-DD HH:MM:SS`. The code 
chunk below takes care of this requirement.

```{r error-date-format, echo=TRUE, tidy=TRUE}
# add a column that has date and time for razimuth package
erData <- add_column(erData, datetime = as.POSIXct(paste(erData$Date, erData$Time_O), format="%Y-%m-%d %H:%M:%S", tz = "America/St_Johns", usetz = TRUE)) 
head(erData)
# select only those columns necessary for ATM calculation
erData <- erData %>%
  dplyr::select(., c(-Alive, -Point, -GID_O, -UTM_Zone, -Time, -Wind, -Rain, -Temperature, -Clouds)) %>% dplyr::select(., ID, GID, Frequency, datetime, Azimuth, prior_r, Line, Observer, TrueLoc, Easting:UTMZone, Date:Time_O, Notes)
# rename columns to appropriate headers for ATM calculation
erData <- erData %>%
  dplyr::rename(indiv = ID, obs_id = GID, azimuth = Azimuth, date = datetime, utm_x = Easting, utm_y = Northing)
```

Now, we are going to convert the `erData` dataframe to a list of `atm` objects
using the `convert_atm` function. We then look at the geometry of each
triangulation attempt using the `visualize_atm` function. 

```{r atm-prep-and-vis, echo=TRUE,tidy=TRUE, message=FALSE}
# AR helped with this code - github.com/robitalec
# For all individuals 
# Unique individuals
eruids <- unique(erData$indiv)

## Convert all to atm
# Loop through 'em
erlsatms <- lapply(eruids, function(id) convert_atm(df = erData[erData$indiv == id,]))

# Name the list for downstream
names(erlsatms) <- eruids

## Visualize all and save all in folder
lapply(seq_along(erlsatms), function(x) {
  # first create an object to store the path to the saving location and the saved object's name
  # we want to save in '../Results/Init_Triangd"
  # we also want to save each plot in a single multipage PDF file, names after
  # the collar being visualized 
  mypath <- file.path("..","Results", "Error_Triangd",paste("error_init_triangulation_", names(erlsatms)[[x]],
                                                           ".pdf", sep = ""))
  # now start the printing device
  pdf(mypath)
  # call a new plot
  plot.new()
  # set the file's name, i.e. the collar frequency, which will appear on the first page of the PDF
  mtext(names(erlsatms)[[x]])
  # now loop through the collar's relocations, one at the time, and plot its geometry
  lapply(erlsatms[[x]]$pid, function(i) visualize_atm(erlsatms[[x]], obs_id = i, add_prior = TRUE))
  # turn off the printing device
  invisible(dev.off())
})
```

## Azimuthal Telemetry Model fitting

`razimuth` performs triangulation and error ellipses estimation around each 
location using an Azimuthal Telemetry Model (ATM; @Gerber2018). The ATM uses a 
Markov Chain Monte Carlo algorithm to iteratively estimate the location of a 
collar based on the azimuthal data over multiple time step. 

> **Note**: This step can be time consuming and computationally 
intensive. On a machine with a Quad-Core Intel Core i7 2.5 GHz with 16 Gb RAM, 
it took about **20 minutes**. Please, allocate as much or more time to complete 
running or compiling this code chunk, depending on your hardware configuration. 

> We provide a pre-generated `.rds` file to load in your R code if you do not 
want or cannot run this portion of the code. The pre-generated file can be 
found here: 
`../Results/razimuth_errorT_lsfits.rds`

```{r error-atm-fit, eval=FALSE, tidy=TRUE, results='hide'}
tictoc::tic() # start timing how long it will take to run
# Model all
erlsfits <- lapply(erlsatms, atm_mcmc, n_mcmc = 10000, n_burn = 1000)
tictoc::toc() # return total run time
```

Given the extremely long runtime of the above code chunk, saving its output is a
good idea to save time in future iterations of this notebook.

```{r error-atm-fits-save, eval=FALSE, tidy=TRUE, message=FALSE, results="hide"}
# save the resulting model fits as and .rds object
# this step allows us to not run the whole code each time, instead
# skipping ahead of the most computational intensive part
erlsfits <- saveRDS(erlsfits, "../Results/razimuth_errorT_lsfits.rds")
```

### Visual check of the triangulations

Now, let's load the model fits and visualize the output of the ATM, with the errors.

```{r error-atm-fits-loading, echo=TRUE,tidy=TRUE}
erlsfits <- readRDS("../Results/razimuth_errorT_lsfits.rds")
```

First, we plot each triangulations with its associated error ellipses, 
error estimates, and posterior-estimated location of the collar. As before, 
to accommodate the large number of plots produced by the following code chunk,
we are going to save them in a dedicate folder, `Post_Triangd`, under `Results`.

```{r error-trials-atm-error-vis, echo=TRUE, tidy=TRUE, message=FALSE, results="hide"}
# Visualize all with error
# 
lapply(seq_along(erlsatms), function(x) {
  mypath <- file.path("..","Results", "Error_Triangd",paste("error_post_triangulation_", names(erlsatms)[[x]],
                                                           ".pdf", sep = ""))
  pdf(mypath)
  print(plot.new())
  mtext(names(erlsatms)[[x]])
  lapply(erlsatms[[x]]$pid, plyr::failwith(NULL, function(i) {
    visualize_atm(erlsatms[[x]], obs_id = i, add_prior = TRUE)
    p_isopleth(df = erlsfits[[x]]$mu_ls[[i]]$pdraws, prob_lvls = c(0.95), range_extend = 0,
               kde_n = 50, col_vec = c(4,4))
    points(matrix(erlsfits[[x]]$pmode[i, 2:3], ncol = 2), pch = 21, bg = 4)
    legend("topleft", c("Posterior Mode"), pch = 21, pt.bg = 4, bty = "n")
  }
  ))
  invisible(dev.off())
})
```

A way to assess how good the fit of the ATM to our data was is to plot the
values of the parameter kappa over each iteration. We can do this in two ways:
either in a traceplot, which shows the variation in the value of kappa, or as a 
running mean, which show the change in the mean value of kappa over each 
iteration. First, let's look at the traceplot for kappa. Here, we are looking for
a plot in which the peaks and pits are, in general, about the same width. 
We save the resulting graphs in folder `Results` as a single file named 
`error_traceplot.pdf`.

``` {r error-kappa-convergence-check-1, echo=TRUE, tidy=TRUE}
# check convergence ----
# pdf('../Results/error_traceplot.pdf')
par(mar = c(2,2,2,2), mfrow = c(5,3))
lapply(seq_along(erlsfits), function(x) {
  # plot.new()
  plot_kappa(atm_obj = erlsfits[[x]]$kappa_ls, item = "traceplot")
  mtext(names(erlsfits)[[x]], line = 0.5)
})
# dev.off()
```

And here we plot the running mean of kappa. In this case, we are looking for 
a line that eventually flattens out. We save the resulting graphs in folder 
`Results` as a single file named `error_runmean.pdf`.

```{R error-kappa-convergence-check-2, echo=TRUE, tidy=TRUE}
# pdf('../Results/error_runmean.pdf')
par(mar = c(2,2,2,2), mfrow = c(5,3))
lapply(seq_along(erlsfits), function(x) {
  # plot.new()
  plot_kappa(atm_obj = erlsfits[[x]]$kappa_ls, item = "run_mean")
  mtext(names(erlsfits)[[x]], line = 0.5)
})
# dev.off()
```

### Data Error Extraction

Now that the triangulation is complete, what is left to do is to extract the
variances associated with each relocation to use them with `ctmm` to estimate 
and error-corrected home range size.

```{r error-vars-extract, echo=TRUE, tidy=TRUE}
## Extract variances to use in ctmm
erlsvars <- lapply(seq_along(erlsfits), function(x) {
  rbindlist(lapply(erlsfits[[x]]$mu_ls, function(y) {
    xy <- y[['pdraws']]
    data.table(COVt.x.y = var(x=xy[,1], y=xy[,2]), pid = y[['pid']], 
               COV.x.x = var(xy[, 1]), COV.y.y = var(xy[, 2]))
  }))[, id := names(erlsfits)[[x]]]
})

# bind into a list
errorTrials.vars <- rbindlist(erlsvars)
```

We now create a new dataframe that contains the relocations, collar IDs, and 
variances from `atm_mcmc()`.

```{r echo=TRUE,tidy=TRUE}
# create a dataframe with relocations, IDs, and variances 
# extract relocation data
erlsreloc <- lapply(seq_along(erlsfits), function(x) {
  rbindlist(lapply(erlsfits[[x]]$mu_ls, function(y) {
    xy <- as.matrix(y[['pmode']])
    data.table(utm_x = xy[1,], utm_y=xy[2,], pid = y[['pid']])
  }))[, id := names(erlsfits)[[x]]]
})

errorTrials.relocs <- rbindlist(erlsreloc)
# join vars and relocs based on date
# add new column of collar, pid to be joined by 
errorTrials.vars <- errorTrials.vars %>% tidyr::unite(cpid, c(id,pid), sep=',', remove=F)
errorTrials.relocs <- errorTrials.relocs %>% tidyr::unite(cpid, c(id,pid), sep=',', remove=F)
errorTrials.atm <- full_join(errorTrials.vars, errorTrials.relocs, by='cpid', keep=FALSE)
```

To work in the Movebank format required by package `ctmm`, we need to add a 
date-time stamp for each relocation. We will first get this information from the
`vhfData` object created above, then add it to the `hares.atm` dataframe we 
just created.

```{r date-time-stamp, echo=TRUE, tidy=TRUE}
# now need to get date-time stamp for each reloc for MoveBank 
# get the first date-time for each indiv/obs_id from vhfData
dates <- erData %>% 
  dplyr::group_by(indiv, obs_id) %>%
  dplyr::filter(row_number()==1) %>%
  tidyr::unite(cpid, c(indiv, obs_id), sep=',', remove=F) %>%
  dplyr::select(c(-utm_x, -utm_y, -azimuth, -prior_r, -obs_id, -indiv))
trials.triangd <- left_join(errorTrials.atm, dates, by='cpid', keep=FALSE)
```


## Error measurements

Now that all error trials have been triangulated, we can estimate the distance
between a collar's true location and the location estimated from MR's or BS's
triangulation efforts. We use function `st_distance` from package `sf` to measure 
the distance then, for each observer, we extract mean, median, minimum, and
maximum error, as well as the standard deviation.

```{r error-reduction-dist, echo=TRUE, tidy=TRUE}
# load dataset with true locations of test collars
trueLocs_raw <- read.csv("../Data/ErrorTrials_TrueLocs.csv")

trueLocs_raw$TrueLoc <- as.factor(trueLocs_raw$TrueLoc)

# set coordinates with an up to date datum
trueLocs <- drop_na(trueLocs_raw, Easting)
coordinates(trueLocs) <- c("Easting", "Northing")
proj4string(trueLocs) <- CRS("+init=epsg:32622")

trueLocs <- spTransform(trueLocs, CRS("+proj=tmerc +lat_0=0 +lon_0=-61.5 +k=0.9999 +x_0=304800 +y_0=0 +ellps=GRS80 +units=m +no_defs"))

# turn the triangulated locations objects into a sp object
trials.triangd_sp <- SpatialPointsDataFrame(coords = trials.triangd[, c("utm_x", "utm_y")], data = trials.triangd[, c(1:6, 9:24)], proj4string = CRS("+proj=tmerc +lat_0=0 +lon_0=-61.5 +k=0.9999 +x_0=304800 +y_0=0 +ellps=GRS80 +units=m +no_defs"))


# turn it into a sf object to use st_distance to calculate distance between tests 
# and true locs
trueLocs_sf <- st_as_sf(trueLocs) %>% rename(., Frequency = Collar) %>% arrange(., Date, Frequency)

rr <- c(23L, 24L, 26L, 27L, 28L, 29L)

trials.triangd_sf <- st_as_sf(trials.triangd_sp) %>% arrange(., Date, Frequency) %>% dplyr::filter(., !(row_number() %in% rr))

# now, measure the distance in meters, between trials and true locations
trials.triangd_sf$Error <- as.numeric(st_distance(trials.triangd_sf, trueLocs_sf, by_element = TRUE, which = "Euclidean"))

# and get a mean value
err_mean <- with(trials.triangd_sf, tapply(trials.triangd_sf$Error, trials.triangd_sf$Observer, mean))
err_sd <- with(trials.triangd_sf, tapply(trials.triangd_sf$Error, trials.triangd_sf$Observer, sd))
err_min <- with(trials.triangd_sf, tapply(trials.triangd_sf$Error, trials.triangd_sf$Observer, min))
err_max <- with(trials.triangd_sf, tapply(trials.triangd_sf$Error, trials.triangd_sf$Observer, max))
err_median <- with(trials.triangd_sf, tapply(trials.triangd_sf$Error, trials.triangd_sf$Observer, median))


# remove temporary object that will be used later on

# rm(list = c("IDs", "UniqIDs", "TmpInds", "TmpData", "current.triang", 
#             "current.triang.dat", "current.triang.index", "current.triang.int", 
#             "current.triang.loc", "workingCollar.coords", "workingCollar.loc", 
#             "workingCollar.spatial", "date"))
```

Thus, according to our analyses, the mean error for MR in 2017 was 
**`r prettyNum(err_mean[2], digits = 3)` $\pm$ `r prettyNum(err_sd[2], digits = 3)`** m, 
whereas for BS in 2018 it was 
**`r prettyNum(err_mean[1], digits = 3)` $\pm$ `r prettyNum(err_sd[1], digits = 3)`** m.