---
title: "Home Range Overlap"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: "Matteo Rizzuto"
output:
  rmdformats::html_clean:
    self_contained: false
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
    fig_width: 8
    fig_height: 6
    df_print: paged
  pdf_document:
    citation_package: biblatex
    dev: pdf
    fig_caption: true
    fig_crop: TRUE
    highlight: tango
    keep_tex: true
    latex_engine: pdflatex
    toc: true
    toc_depth: 2
    number_sections: false
    df_print: kable    
fontsize: 11pt
geometry: margin=1in
documentclass: article    
bibliography: ../bibliography.bib
csl: ../oikos.csl
editor_options: 
  chunk_output_type: inline
---

```{r shpfile-load, echo=TRUE, tidy=TRUE}
# read the forest shapefile from the Land Cover geodatabase
forest_gdb <- read_sf("../../Mapping", layer = "Forest")

forest_clip <- st_crop(forest_gdb, e)
```

## Utilization Distribution Overlap across years

The code below allows us to assess the overlap in the kUD of the four
individuals with 2 years each of telemetry sampling [@Fieberg2006]. `ctmm` 
allows for assessing the overlap of two Utilization Distributions using the
Bhattacharyya's affinity index (henceforth, `BA`). The function `overlap`
computes the value of `BA` and return the overlap of the autocorrelated 
kernel density estimators. The four hares had different collar frequencies 
between sampling years:

Eat Tag       Collar Frequency        Year
-------       ----------------        ----
A3769         149.653                 2018
A3769         150.173                 2019
A1698         149.053                 2018
A1698         149.294                 2019
A3719         149.535                 2017
A3719         149.003                 2018
A3769         149.274                 2018
A3769         150.314                 2019

In the code below, we first isolate the utilization distribution of the four 
snowshoe hares for which we have two years of telemetry sampling, then apply
the function `overlap`. We provide the results of this analysis in the SI Table 
S4, so we report here only the code necessary to produce the table.

### A1425

```{r hr-overlap-A1425, echo=TRUE, tidy=TRUE}
# create a list to store the two UDs
A1425_uds <- list()

# populate the list
A1425_uds[[1]] <- homeRanges[['149.653']]
A1425_uds[[2]] <- homeRanges[['150.173']]

# assign names to list based on year of sampling
names(A1425_uds) <- c("2018", "2019")

# calculate UDs overlap with the Bhattacharyya's affinity index
A1425_olap <- overlap(A1425_uds, level = 0.95, debias=TRUE)

# visualize the array of results
A1425_olap 

# convert the array to a dataframe
A1425_olap_df <- adply(A1425_olap, c(1,2)) %>% dplyr::rename(., UD1=X1, UD2=X2) %>% dplyr::select(., UD1, UD2, est) 

A1425_olap_df$EarTag <- "A1425"
```

Now, let's visualize the overlap. The code below produces figure S3 in the 
Supplementary Information; as such, we only provide the code top produce it here.

```{r overlap-A1425-fig, echo=TRUE, tidy=TRUE, message=FALSE}
# extract the UD contours at 50%, 75%, and 90% isopleths
A1425.50 <- lapply(1:length(A1425_uds), function(x) SpatialPolygonsDataFrame.UD(A1425_uds[[x]], level.UD=0.50, level = 0.95))

A1425.75 <- lapply(1:length(A1425_uds), function(x) SpatialPolygonsDataFrame.UD(A1425_uds[[x]], level.UD=0.75, level = 0.95))

A1425.90 <- lapply(1:length(A1425_uds), function(x) SpatialPolygonsDataFrame.UD(A1425_uds[[x]], level.UD=0.90, level = 0.95))

# remove unnecessary polygons and rows, we are only interested in the real 
# estimate not the 95% confidence intervals
# 50%
A1425.50[[1]]@polygons[c(1,3)] <- NULL
A1425.50[[1]]@data$name[c(1,3)] <- NA
A1425.50[[1]]@data <- drop_na(A1425.50[[1]]@data)
A1425.50[[1]]@data$id <- "50%"
A1425.50[[2]]@polygons[c(1,3)] <- NULL
A1425.50[[2]]@data$name[c(1,3)] <- NA
A1425.50[[2]]@data <- drop_na(A1425.50[[2]]@data)
A1425.50[[2]]@data$id <- "50%"

#75%
A1425.75[[1]]@polygons[c(1,3)] <- NULL
A1425.75[[1]]@data$name[c(1,3)] <- NA
A1425.75[[1]]@data <- drop_na(A1425.75[[1]]@data)
A1425.75[[1]]@data$id <- "75%"
A1425.75[[2]]@polygons[c(1,3)] <- NULL
A1425.75[[2]]@data$name[c(1,3)] <- NA
A1425.75[[2]]@data <- drop_na(A1425.75[[2]]@data)
A1425.75[[2]]@data$id <- "75%"

#90%
A1425.90[[1]]@polygons[c(1,3)] <- NULL
A1425.90[[1]]@data$name[c(1,3)] <- NA
A1425.90[[1]]@data <- drop_na(A1425.90[[1]]@data)
A1425.90[[1]]@data$id <- "90%"
A1425.90[[2]]@polygons[c(1,3)] <- NULL
A1425.90[[2]]@data$name[c(1,3)] <- NA
A1425.90[[2]]@data <- drop_na(A1425.90[[2]]@data)
A1425.90[[2]]@data$id <- "90%"
  
# rbind UD estimates into a single SPDF
A1425.2018 <- rbind(A1425.50[[1]], A1425.75[[1]], A1425.90[[1]])
A1425.2019 <- rbind(A1425.50[[2]], A1425.75[[2]], A1425.90[[2]])

# convert UD estimates to SpatialLinesDataFrame
A1425.2018.cont <- as(A1425.2018, "SpatialLinesDataFrame")
A1425.2019.cont <- as(A1425.2019, "SpatialLinesDataFrame")

# convert home range contour lines to sf objects
A1425.2018.contSf <- st_as_sf(A1425.2018.cont)
A1425.2019.contSf <- st_as_sf(A1425.2019.cont)

# create a dedicated bounding box for the map
bbox_temp <- st_bbox(A1425.2018.contSf) # current bounding box
    
    xrange <- bbox_temp$xmax - bbox_temp$xmin # range of x values
    yrange <- bbox_temp$ymax - bbox_temp$ymin # range of y values
    
    bbox_temp[1] <- bbox_temp[1] - (0.05 * xrange) # xmin - left
    bbox_temp[3] <- bbox_temp[3] + (0.05 * xrange) # xmax - right
    bbox_temp[2] <- bbox_temp[2] - (0.05 * yrange) # ymin - bottom
    bbox_temp[4] <- bbox_temp[4] + (0.05 * yrange) # ymax - top
    
    bbox_temp <- bbox_temp %>%  # take the bounding box ...
      st_as_sfc() # ... and make it a sf polygon

# map it
olapmap_A1425 <- 
    tm_shape(forest_clip, bbox = bbox_temp) +
        tm_borders(col = "grey") +
    tm_shape(bl_grid_pts) +
    tm_dots(size = 0.75, shape = 18, col = "red", alpha = 0.3) + # grid trap locs
    tm_shape(A1425.2018.contSf) +
    tm_lines(col = "id", palette = c("#a6611a", "#dfc27d"), title.col = " % 2018 UD", lwd = 2) +
    tm_shape(A1425.2019.contSf) + 
    tm_lines(col = "id", palette = c("#018571", "#80cdc1"), title.col = "% 2019 UD", lwd = 2) +
    tm_compass(position = c("right", "top")) +
    tm_scale_bar(width = 0.3, 
                 text.size = 1.25,
                 position = c("right", "bottom")) + 
    tm_layout(legend.outside = TRUE, 
              legend.outside.position = "right",
              legend.text.size = 1.1,
              legend.title.size = 1.25,
              asp = 1,
              frame = TRUE)
    
# tmap_save(olapmap_A1425, filename = "../Results/A1425_overlap.pdf", dpi = 600) 
```


### A1698
```{r hr-overlap-A1698, echo=TRUE, tidy=TRUE}
# create a list to store the two UDs
A1698_uds <- list()

# populate the list
A1698_uds[[1]] <- homeRanges[['149.053']]
A1698_uds[[2]] <- homeRanges[['149.294']]

# assign names to list based on year of sampling
names(A1698_uds) <- c("2018", "2019")

# calculate UDs overlap with the Bhattacharyya's affinity index
A1698_olap <- overlap(A1698_uds, level = 0.95, debias=TRUE)

# visualize the array of results
A1698_olap 

# convert the array to a dataframe
A1698_olap_df <- adply(A1698_olap, c(1,2)) %>% dplyr::rename(., UD1=X1, UD2=X2) %>% dplyr::select(., UD1, UD2, est) 

A1698_olap_df$EarTag <- "A1698"
```

Now, let's visualize the overlap. The code below produces figure S3 in the 
Supplementary Information; as such, we only provide the code top produce it here.

```{r overlap-A1698-fig, echo=TRUE, tidy=TRUE, message=FALSE}
# extract the UD contours at 50%, 75%, and 90% isopleths
A1698.50 <- lapply(1:length(A1698_uds), function(x) SpatialPolygonsDataFrame.UD(A1698_uds[[x]], level.UD=0.50, level = 0.95))

A1698.75 <- lapply(1:length(A1698_uds), function(x) SpatialPolygonsDataFrame.UD(A1698_uds[[x]], level.UD=0.75, level = 0.95))

A1698.90 <- lapply(1:length(A1698_uds), function(x) SpatialPolygonsDataFrame.UD(A1698_uds[[x]], level.UD=0.90, level = 0.95))

# remove unnecessary polygons and rows, we are only interested in the real 
# estimate not the 95% confidence intervals
# 50%
A1698.50[[1]]@polygons[c(1,3)] <- NULL
A1698.50[[1]]@data$name[c(1,3)] <- NA
A1698.50[[1]]@data <- drop_na(A1698.50[[1]]@data)
A1698.50[[1]]@data$id <- "50%"
A1698.50[[2]]@polygons[c(1,3)] <- NULL
A1698.50[[2]]@data$name[c(1,3)] <- NA
A1698.50[[2]]@data <- drop_na(A1698.50[[2]]@data)
A1698.50[[2]]@data$id <- "50%"

#75%
A1698.75[[1]]@polygons[c(1,3)] <- NULL
A1698.75[[1]]@data$name[c(1,3)] <- NA
A1698.75[[1]]@data <- drop_na(A1698.75[[1]]@data)
A1698.75[[1]]@data$id <- "75%"
A1698.75[[2]]@polygons[c(1,3)] <- NULL
A1698.75[[2]]@data$name[c(1,3)] <- NA
A1698.75[[2]]@data <- drop_na(A1698.75[[2]]@data)
A1698.75[[2]]@data$id <- "75%"

#90%
A1698.90[[1]]@polygons[c(1,3)] <- NULL
A1698.90[[1]]@data$name[c(1,3)] <- NA
A1698.90[[1]]@data <- drop_na(A1698.90[[1]]@data)
A1698.90[[1]]@data$id <- "90%"
A1698.90[[2]]@polygons[c(1,3)] <- NULL
A1698.90[[2]]@data$name[c(1,3)] <- NA
A1698.90[[2]]@data <- drop_na(A1698.90[[2]]@data)
A1698.90[[2]]@data$id <- "90%"
  
# rbind UD estimates into a single SPDF
A1698.2018 <- rbind(A1698.50[[1]], A1698.75[[1]], A1698.90[[1]])
A1698.2019 <- rbind(A1698.50[[2]], A1698.75[[2]], A1698.90[[2]])

# convert UD estimates to SpatialLinesDataFrame
A1698.2018.cont <- as(A1698.2018, "SpatialLinesDataFrame")
A1698.2019.cont <- as(A1698.2019, "SpatialLinesDataFrame")

# convert home range contour lines to sf objects
A1698.2018.contSf <- st_as_sf(A1698.2018.cont)
A1698.2019.contSf <- st_as_sf(A1698.2019.cont)

# create a dedicated bounding box for the map
bbox_temp <- st_bbox(A1698.2019.contSf) # current bounding box
    
    xrange <- bbox_temp$xmax - bbox_temp$xmin # range of x values
    yrange <- bbox_temp$ymax - bbox_temp$ymin # range of y values
    
    bbox_temp[1] <- bbox_temp[1] - (0.05 * xrange) # xmin - left
    bbox_temp[3] <- bbox_temp[3] + (0.05 * xrange) # xmax - right
    bbox_temp[2] <- bbox_temp[2] - (0.05 * yrange) # ymin - bottom
    bbox_temp[4] <- bbox_temp[4] + (0.05 * yrange) # ymax - top
    
    bbox_temp <- bbox_temp %>%  # take the bounding box ...
      st_as_sfc() # ... and make it a sf polygon

# map it
olapmap_A1698 <- 
    tm_shape(forest_clip, bbox = bbox_temp) +
        tm_borders(col = "grey") +
    tm_shape(bl_grid_pts) +
    tm_dots(size = 0.75, shape = 18, col = "red", alpha = 0.3) + # grid trap locs
    tm_shape(A1698.2018.contSf) + 
    tm_lines(col = "id", palette = c("#a6611a", "#dfc27d"), title.col = " % 2018 UD", lwd = 2) +
    tm_shape(A1698.2019.contSf, is.master = T) + 
    tm_lines(col = "id", palette = c("#018571", "#80cdc1"), title.col = "% 2019 UD", lwd = 2) +
    tm_compass(position = c("right", "top")) +
    tm_scale_bar(width = 0.3, 
                 text.size = 1.25,
                 position = c("right", "bottom")) + 
    tm_layout(legend.outside = TRUE, 
              legend.outside.position = "right",
              legend.text.size = 1.1,
              legend.title.size = 1.25,
              asp = 1,
              frame = TRUE)
    
# tmap_save(olapmap_A1698, filename = "../Results/A1698_overlap.pdf", dpi = 600)   
```

### A3719
```{r hr-overlap-A3719, echo=TRUE, tidy=TRUE}
# create a list to store the two UDs
A3719_uds <- list()

# populate the list
A3719_uds[[1]] <- homeRanges[['149.535']]
A3719_uds[[2]] <- homeRanges[['149.003']]

# assign names to list based on year of sampling
names(A3719_uds) <- c("2017", "2018")

# calculate UDs overlap with the Bhattacharyya's affinity index
A3719_olap <- overlap(A3719_uds, level = 0.95, debias=TRUE)

# visualize the array of results
A3719_olap 

# convert the array to a dataframe
A3719_olap_df <- adply(A3719_olap, c(1,2)) %>% dplyr::rename(., UD1=X1, UD2=X2) %>% dplyr::select(., UD1, UD2, est) 

A3719_olap_df$EarTag <- "A3719"
```

Now, let's visualize the overlap. The code below produces figure S3 in the 
Supplementary Information; as such, we only provide the code top produce it here.

```{r overlap-A3719-fig, echo=TRUE, tidy=TRUE, message=FALSE}
# extract the UD contours at 50%, 75%, and 90% isopleths
A3719.50 <- lapply(1:length(A3719_uds), function(x) SpatialPolygonsDataFrame.UD(A3719_uds[[x]], level.UD=0.50, level = 0.95))

A3719.75 <- lapply(1:length(A3719_uds), function(x) SpatialPolygonsDataFrame.UD(A3719_uds[[x]], level.UD=0.75, level = 0.95))

A3719.90 <- lapply(1:length(A3719_uds), function(x) SpatialPolygonsDataFrame.UD(A3719_uds[[x]], level.UD=0.90, level = 0.95))

# remove unnecessary polygons and rows, we are only interested in the real 
# estimate not the 95% confidence intervals
# 50%
A3719.50[[1]]@polygons[c(1,3)] <- NULL
A3719.50[[1]]@data$name[c(1,3)] <- NA
A3719.50[[1]]@data <- drop_na(A3719.50[[1]]@data)
A3719.50[[1]]@data$id <- "50%"
A3719.50[[2]]@polygons[c(1,3)] <- NULL
A3719.50[[2]]@data$name[c(1,3)] <- NA
A3719.50[[2]]@data <- drop_na(A3719.50[[2]]@data)
A3719.50[[2]]@data$id <- "50%"

#75%
A3719.75[[1]]@polygons[c(1,3)] <- NULL
A3719.75[[1]]@data$name[c(1,3)] <- NA
A3719.75[[1]]@data <- drop_na(A3719.75[[1]]@data)
A3719.75[[1]]@data$id <- "75%"
A3719.75[[2]]@polygons[c(1,3)] <- NULL
A3719.75[[2]]@data$name[c(1,3)] <- NA
A3719.75[[2]]@data <- drop_na(A3719.75[[2]]@data)
A3719.75[[2]]@data$id <- "75%"

#90%
A3719.90[[1]]@polygons[c(1,3)] <- NULL
A3719.90[[1]]@data$name[c(1,3)] <- NA
A3719.90[[1]]@data <- drop_na(A3719.90[[1]]@data)
A3719.90[[1]]@data$id <- "90%"
A3719.90[[2]]@polygons[c(1,3)] <- NULL
A3719.90[[2]]@data$name[c(1,3)] <- NA
A3719.90[[2]]@data <- drop_na(A3719.90[[2]]@data)
A3719.90[[2]]@data$id <- "90%"
  
# rbind UD estimates into a single SPDF
A3719.2017 <- rbind(A3719.50[[1]], A3719.75[[1]], A3719.90[[1]])
A3719.2018 <- rbind(A3719.50[[2]], A3719.75[[2]], A3719.90[[2]])

# convert UD estimates to SpatialLinesDataFrame
A3719.2017.cont <- as(A3719.2017, "SpatialLinesDataFrame")
A3719.2018.cont <- as(A3719.2018, "SpatialLinesDataFrame")

# convert home range contour lines to sf objects
A3719.2017.contSf <- st_as_sf(A3719.2017.cont)
A3719.2018.contSf <- st_as_sf(A3719.2018.cont)

# create a dedicated bounding box for the map
bbox_temp <- st_bbox(A3719.2018.contSf) # current bounding box
    
    xrange <- bbox_temp$xmax - bbox_temp$xmin # range of x values
    yrange <- bbox_temp$ymax - bbox_temp$ymin # range of y values
    
    bbox_temp[1] <- bbox_temp[1] - (0.05 * xrange) # xmin - left
    bbox_temp[3] <- bbox_temp[3] + (0.05 * xrange) # xmax - right
    bbox_temp[2] <- bbox_temp[2] - (0.05 * yrange) # ymin - bottom
    bbox_temp[4] <- bbox_temp[4] + (0.05 * yrange) # ymax - top
    
    bbox_temp <- bbox_temp %>%  # take the bounding box ...
      st_as_sfc() # ... and make it a sf polygon

# map it
olapmap_A3719 <- 
    tm_shape(forest_clip, bbox = bbox_temp) +
        tm_borders(col = "grey") +
    tm_shape(bl_grid_pts) +
    tm_dots(size = 0.75, shape = 18, col = "red", alpha = 0.3) + # grid trap locs
    tm_shape(A3719.2017.contSf) + 
    tm_lines(col = "id", palette = c("#a6611a", "#dfc27d"), title.col = " % 2017 UD", lwd = 2) +
    tm_shape(A3719.2018.contSf, is.master = TRUE) + 
    tm_lines(col = "id", palette = c("#018571", "#80cdc1"), title.col = "% 2018 UD", lwd = 2) +
    tm_compass(position = c("right", "top")) +
    tm_scale_bar(width = 0.3, 
                 text.size = 1.25,
                 position = c("right", "bottom")) + 
    tm_layout(
              # main.title = paste("Collar Frequency:", loopCIDs[i]),
              # title = paste("Ear tag:", dots.temp$EarTag),
              legend.outside = TRUE, 
              legend.outside.position = "right",
              legend.text.size = 1.1,
              legend.title.size = 1.25,
              asp = 1,
              frame = TRUE)
    
# tmap_save(olapmap_A3719, filename = "../Results/A3719_overlap.pdf", dpi = 600)
```

### A3769
```{r hr-overlap-A3769, echo=TRUE, tidy=TRUE}
# create a list to store the two UDs
A3769_uds <- list()

# populate the list
A3769_uds[[1]] <- homeRanges[['149.274']]
A3769_uds[[2]] <- homeRanges[['150.314']]

# assign names to list based on year of sampling
names(A3769_uds) <- c("2018", "2019")

# calculate UDs overlap with the Bhattacharyya's affinity index
A3769_olap <- overlap(A3769_uds, level = 0.95, debias=TRUE)

# visualize the array of results
A3769_olap

# convert the array to a dataframe
A3769_olap_df <- adply(A3769_olap, c(1,2)) %>% dplyr::rename(., UD1=X1, UD2=X2) %>% dplyr::select(., UD1, UD2, est) 

A3769_olap_df$EarTag <- "A3769"
```

Now, let's visualize the overlap. The code below produces figure S3 in the 
Supplementary Information; as such, we only provide the code top produce it here.

```{r overlap-A3769-fig, echo=TRUE, tidy=TRUE, message=FALSE}
# extract the UD contours at 50%, 75%, and 90% isopleths
A3769.50 <- lapply(1:length(A3769_uds), function(x) SpatialPolygonsDataFrame.UD(A3769_uds[[x]], level.UD=0.50, level = 0.95))

A3769.75 <- lapply(1:length(A3769_uds), function(x) SpatialPolygonsDataFrame.UD(A3769_uds[[x]], level.UD=0.75, level = 0.95))

A3769.90 <- lapply(1:length(A3769_uds), function(x) SpatialPolygonsDataFrame.UD(A3769_uds[[x]], level.UD=0.90, level = 0.95))

# remove unnecessary polygons and rows, we are only interested in the real 
# estimate not the 95% confidence intervals
# 50%
A3769.50[[1]]@polygons[c(1,3)] <- NULL
A3769.50[[1]]@data$name[c(1,3)] <- NA
A3769.50[[1]]@data <- drop_na(A3769.50[[1]]@data)
A3769.50[[1]]@data$id <- "50%"
A3769.50[[2]]@polygons[c(1,3)] <- NULL
A3769.50[[2]]@data$name[c(1,3)] <- NA
A3769.50[[2]]@data <- drop_na(A3769.50[[2]]@data)
A3769.50[[2]]@data$id <- "50%"

#75%
A3769.75[[1]]@polygons[c(1,3)] <- NULL
A3769.75[[1]]@data$name[c(1,3)] <- NA
A3769.75[[1]]@data <- drop_na(A3769.75[[1]]@data)
A3769.75[[1]]@data$id <- "75%"
A3769.75[[2]]@polygons[c(1,3)] <- NULL
A3769.75[[2]]@data$name[c(1,3)] <- NA
A3769.75[[2]]@data <- drop_na(A3769.75[[2]]@data)
A3769.75[[2]]@data$id <- "75%"

#90%
A3769.90[[1]]@polygons[c(1,3)] <- NULL
A3769.90[[1]]@data$name[c(1,3)] <- NA
A3769.90[[1]]@data <- drop_na(A3769.90[[1]]@data)
A3769.90[[1]]@data$id <- "90%"
A3769.90[[2]]@polygons[c(1,3)] <- NULL
A3769.90[[2]]@data$name[c(1,3)] <- NA
A3769.90[[2]]@data <- drop_na(A3769.90[[2]]@data)
A3769.90[[2]]@data$id <- "90%"
  
# rbind UD estimates into a single SPDF
A3769.2018 <- rbind(A3769.50[[1]], A3769.75[[1]], A3769.90[[1]])
A3769.2019 <- rbind(A3769.50[[2]], A3769.75[[2]], A3769.90[[2]])

# convert UD estimates to SpatialLinesDataFrame
A3769.2018.cont <- as(A3769.2018, "SpatialLinesDataFrame")
A3769.2019.cont <- as(A3769.2019, "SpatialLinesDataFrame")

# convert home range contour lines to sf objects
A3769.2018.contSf <- st_as_sf(A3769.2018.cont)
A3769.2019.contSf <- st_as_sf(A3769.2019.cont)

# create a dedicated bounding box for the map
bbox_temp <- st_bbox(A3769.2018.contSf) # current bounding box
    
    xrange <- bbox_temp$xmax - bbox_temp$xmin # range of x values
    yrange <- bbox_temp$ymax - bbox_temp$ymin # range of y values
    
    bbox_temp[1] <- bbox_temp[1] - (0.05 * xrange) # xmin - left
    bbox_temp[3] <- bbox_temp[3] + (0.05 * xrange) # xmax - right
    bbox_temp[2] <- bbox_temp[2] - (0.05 * yrange) # ymin - bottom
    bbox_temp[4] <- bbox_temp[4] + (0.05 * yrange) # ymax - top
    
    bbox_temp <- bbox_temp %>%  # take the bounding box ...
      st_as_sfc() # ... and make it a sf polygon

# map it
olapmap_A3769 <- 
    tm_shape(forest_clip, bbox = bbox_temp) +
        tm_borders(col = "grey") +
    tm_shape(bl_grid_pts) +
    tm_dots(size = 0.75, shape = 18, col = "red", alpha = 0.3) + # grid trap locs
    tm_shape(A3769.2018.contSf) + 
    tm_lines(col = "id", palette = c("#a6611a", "#dfc27d"), title.col = " % 2018 UD", lwd = 2) +
    tm_shape(A3769.2019.contSf) + 
    tm_lines(col = "id", palette = c("#018571", "#80cdc1"), title.col = "% 2019 UD", lwd = 2) +
    tm_compass(position = c("right", "top")) +
    tm_scale_bar(width = 0.3, 
                 text.size = 1.25,
                 position = c("right", "bottom")) + 
    tm_layout(
              # main.title = paste("Collar Frequency:", loopCIDs[i]),
              # title = paste("Ear tag:", dots.temp$EarTag),
              legend.outside = TRUE, 
              legend.outside.position = "right",
              legend.text.size = 1.1,
              legend.title.size = 1.25,
              asp = 1,
              frame = TRUE)
    
# tmap_save(olapmap_A3769, filename = "../Results/A3769_overlap.pdf", dpi = 600)
```

### Summary Table

The code chunk produces Table S3 in the Supplementary Information. As in other
such cases, we provide here only the code to produce the table and refer readers
to the SI to see the output.

```{r olap-table, tidy=TRUE, results='hide', message=FALSE}
olap <- dplyr::full_join(A1425_olap_df,A1698_olap_df) %>% dplyr::full_join(., A3719_olap_df) %>% dplyr::full_join(., A3769_olap_df) %>% dplyr::rename(., `Bhattacharyya Index` = est)

kable(olap[, 1:3]) %>%  group_rows(index = setNames(rle(olap$EarTag)[[1]], 
                                                    rle(olap$EarTag)[[2]])) %>%
   kable_styling(bootstrap_options = c("hover", "condensed"), 
                 fixed_thead = TRUE) %>% 
   scroll_box(width = "100%", height = "100%")

olap_tab <- gt(olap) %>% 
  fmt_number(., columns = 3, decimals = 3) %>% 
  tab_row_group(., group = "A3769", rows = c(13:16)) %>% 
  tab_row_group(., group = "A3719", rows = c(9:12)) %>% 
  tab_row_group(., group = "A1698", rows = c(5:8)) %>% 
  tab_row_group(., group = "A1425", rows = c(1:4)) %>% 
  cols_hide(., columns = vars(EarTag))

# gtsave(olap_tab, filename = "OverlapTab.tex", path = "../Results")

# gtsave(olap_tab, filename = "OverlapTab.rtf", path = "../Results")
```


