---
title: "Supporting Visuals for Stoichiometry of Home Range"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: "Matteo Rizzuto"
output:
  rmdformats::html_clean:
    self_contained: false
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
    fig_width: 12
    fig_height: 8
    df_print: paged
  pdf_document:
    citation_package: biblatex
    dev: pdf
    fig_caption: true
    fig_width: 7
    fig_height: 2.64
    highlight: tango
    keep_tex: true
    latex_engine: pdflatex
    toc: true
    df_print: kable    
fontsize: 11pt
geometry: margin=1in
documentclass: article    
bibliography: ../Manuscripts/Rizzuto_etal_StoichHomeRanges.bib
csl: ../Manuscripts/functional-ecology.csl
editor_options: 
  chunk_output_type: inline
---

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
# if running as a standalone, change chunk options to evaluation this 
# code chunk
knit("StoichiometryOfHomeRanges.Rmd", tangle = TRUE)
source("StoichiometryOfHomeRanges.R")

knit("razimuthTriangulation.Rmd", tangle = TRUE)
source("razimuthTriangulation.R")

knit("aKDEHomeRangeEstimation.Rmd", tangle = TRUE)
source("aKDEHomeRangeEstimation.R")

knit("ModelStoichHR.Rmd", tangle = TRUE)
source("ModelStoichHR.R")

knit("75kUDHRModels.Rmd", tangle = TRUE)
source("75kUDHRModels.R")

knit("90kUDHRModels.Rmd", tangle = TRUE)
source("90kUDHRModels.R")
```

In this section, we produce both the figures included in the main text and 
additional visual materials to support our project. First, we set package `tmap` 
to plotting mode, so all maps will be shown as plots unless otherwise specified. 
```{r tmap-options, echo=TRUE, tidy=TRUE}
tmap_mode("plot")
```

## Manuscript Figures {.tabset .tabset-fade}

Here we provide the code to produce the main text's Figure 1d and Figure 2. 
First, we need to allocate several vectors containing custom-made lists of 
labels, shapes, and colours to highlight data points representing hares with 2 
years of data collection. 

```{r aes-prep, echo=TRUE, tidy=TRUE}
# Create a set of labels that only contains the ear tag labels for the 
# individuals that had multiple years of triangulation
cf_labs <- as.character(hare.stoich$EarTag) # store ear tag labels in a vector
cf_labs[3:7] <- ""
cf_labs[10:13] <- ""
cf_labs[15:17] <- ""
cf_labs[19:26] <- ""
cf_labs[28:30] <- ""
cf_labs[32:34] <- ""

# create vectors to assign shapes to data points in graph
pair_shapes <- rep(21, 34)
names(pair_shapes) <- sort(hare.stoich$EarTag)
pair_shapes[c(2, 3)] <- 22
pair_shapes[c(11, 12)] <- 23
pair_shapes[c(31, 32)] <- 24
pair_shapes[c(33, 34)] <- 25


# repeat but this time for colors
colorCount <- length(hare.stoich$EarTag)
pair_colors <- colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(colorCount)
names(pair_colors) <- sort(hare.stoich$EarTag)

pair_colors[c(2, 3)] <- "#79B1D3"
pair_colors[c(11, 12)] <- "#B89B74"
pair_colors[c(31, 32)] <- "#FFFF99"
pair_colors[c(33, 34)] <- "#CB904D"
```


Now, we can create the plots. Note that we only show the code necessary to produce
each figure in the main text here, not the figure itself. 

### Figure 1d
```{r fig1d, echo=TRUE, tidy=TRUE}
vis1 <- ggplot(hare.stoich, aes(x = VAAN_CN_mean, y = VAAN_CN_CVar)) + 
  geom_point(aes(fill = EarTag, shape = EarTag, size = HRsize)) + 
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  scale_size_continuous(name = "Home Range (ha)", range = c(3,12), breaks = scales::pretty_breaks(3)) +
  xlab("Average Blueberry C:N") + 
  ylab("Blueberry C:N CV") + 
  guides(fill = guide_legend(override.aes = list(size=5)), size = guide_legend(override.aes = list(shape = 21))) +
  geom_text_repel(aes(x = VAAN_CN_mean, y = VAAN_CN_CVar, label = EarTag), size = 5, box.padding = 1.25) + 
  theme_classic() + theme(text = element_text(size = 35), legend.position = "bottom", legend.box = "vertical", legend.box.just = "left")

# ggsave(vis1, filename = "../Results/MeanvsCV_vaanCN.pdf", device = "pdf", dpi = 600, width = 12, height = 18)
```

### Figure 2 

```{r fig2-plots, echo=TRUE, tidy=TRUE}
# Blueberry Mean C:N - 50% kUD
vis2_50kUD <- ggplot(hare.stoich, aes(x = VAAN_CN_mean, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNhr), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) +
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 50% kUD (ha)") + 
  xlab(" ") +
  # geom_text_repel(aes(x = VAAN_CN_mean, y = HRsize, label = EarTag), size = 5) + 
  theme_classic() + theme(text = element_text(size = 22))

# Blueberry Mean C:N - 75% kUD
vis2_75kUD <- ggplot(hare.stoich.75, aes(x = VAAN_CN_mean, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNhr.75), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) +
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 75% kUD (ha)") + 
  xlab("Average Blueberry C:N") +
  # geom_text_repel(aes(x = VAAN_CN_mean, y = HRsize, label = EarTag), size = 5) + 
  theme_classic() + theme(text = element_text(size = 22))

# Blueberry Mean C:N - 90% kUD
vis2_90kUD <- ggplot(hare.stoich.90, aes(x = VAAN_CN_mean, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNhr.90), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) +
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 90% kUD (ha)") + 
  xlab(" ") +
  # geom_text_repel(aes(x = VAAN_CN_mean, y = HRsize, label = EarTag), size = 5) + 
  theme_classic() + theme(text = element_text(size = 22))

# arrange the three "mean" plots into one figure
vis2all <- vis2_50kUD + vis2_75kUD + vis2_90kUD + plot_layout(ncol = 3, nrow = 1, guides = "collect") + plot_annotation(tag_levels = "a", tag_prefix = "(", tag_suffix = ")")
# save it
# ggsave(vis1all, filename = "../Results/HRvAVGvaanCN.png", device = "png", dpi = 300, width = 10, height = 7)

# Blueberry C:N Coefficient of Variation - 50% kUD
vis3_50kUD <- ggplot(hare.stoich, aes(x = VAAN_CN_CVar, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNcvhr), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) + 
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 50% kUD (ha)") + 
  xlab(" ") + 
  # geom_text_repel(aes(x = VAAN_CN_CVar, y = HRsize, label = EarTag), size = 5) + 
  theme_classic() + theme(text = element_text(size = 22))

# Blueberry C:N Coefficient of Variation - 75% kUD
vis3_75kUD <- ggplot(hare.stoich.75, aes(x = VAAN_CN_CVar, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNcvhr.75), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) + 
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 75% kUD (ha)") + 
  xlab("Blueberry C:N CV") + 
  # geom_text_repel(aes(x = VAAN_CN_CVar, y = HRsize, label = EarTag)) + 
  theme_classic() + theme(text = element_text(size = 22))

# Blueberry C:N Coefficient of Variation - 90% kUD
vis3_90kUD <- ggplot(hare.stoich.90, aes(x = VAAN_CN_CVar, y = HRsize)) + 
  geom_smooth(data = fortify(vaanCNcvhr.90), method = "lm", color = "grey", alpha = 0.15, lwd = 2) + 
  geom_point(aes(fill = EarTag, shape = EarTag), size = 8) + 
  scale_fill_manual(name= "Ear tag", 
                    values = pair_colors) +
  scale_shape_manual(name = "Ear tag", 
                     values = pair_shapes) +
  ylab("Home Range size - 90% kUD (ha)") + 
  xlab(" ") + 
  # geom_text_repel(aes(x = VAAN_CN_CVar, y = HRsize, label = EarTag), size = 5) + 
  theme_classic() + theme(text = element_text(size = 22))

# arrange the three "coefficient of variation" plots into a single figure
vis3all <- vis3_50kUD + vis3_75kUD + vis3_90kUD + plot_layout(ncol = 5, nrow = 1, guides = "collect") + plot_annotation(tag_levels = "a", tag_prefix = "(", tag_suffix = ")")
# save it
# ggsave(vis3all, filename = "../Results/HRvVaanCNCVar.png", device = "png", dpi = 300, width = 10, height = 7)

# now, to create Figure 2 in the ms, arrange all six plots just produced into a
# 2 rows by 3 columns figure
visall <- (vis2_50kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + (vis2_75kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + (vis2_90kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + (vis3_50kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + (vis3_75kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + (vis3_90kUD + theme(plot.margin = unit(c(0,12,0,12), "pt"))) + plot_layout(ncol = 3, nrow = 2, guides = "collect", widths = c(1.5, 1.5, 1.5)) + plot_annotation(tag_levels = "a", tag_prefix = "(", tag_suffix = ")")

# save it
ggsave(visall, filename = "../Results/VAAN_HRvsCN.pdf", device = "pdf", dpi = 600, width = 25, height = 15)
```

## Elemental concentrations of N and P in Red Maple and Blueberry

Here we use boxplots to visualize data on the elemental
(% dry weight) composition of both Red Maple and Blueberry. Note that
we report the figure itself in the SI (Figure SXX), so that here we 
only show the code necessary to produce it.

In the code chunk below, we begin by loading the full dataset for the plant SOI
stoichiometry data. This dataset includes the following variables:

* **SampleID**, a unique alphanumeric code that capture the site, location within the site, and species of each sample
* **N**, **P**, **K**, **Mg**, **Ca**, **C** ,the % dry weight content of Nhe corresponding element in a given sample; elements include Nitrogen, Phosphorus, Potassium (K), Magnesium, Calcium, and Carbon
* **SiteCode**, **TrapName**, **Species**, **PlotName**, additional subsetting variables

After loading the dataset, we use `select()` in package `dplyr` to remove 
unnecessary columns and only retain information on site and location within the 
site of collection, Species, and content of N, P, and C. We then `filter` the
dataset to remove information from outside the hare study area (site code 
**BL**). Finally, we use function `ggplot2` and function `geom_boxjitter()` 
from package `ggpol` to plot the stoichiometry data by species in the hare study
area.

```{r acru-vaan-ep, echo=TRUE, tidy=TRUE}
# load the plant stoichiometry data. 
epData <- read.csv("../Data/StoichFromLabAnalysis_Clean_2017Feb25.csv", header = T) %>% as_tibble() %>%
  mutate(., across(where(is.character), str_trim)) %>% 
  mutate_if(., is.character, as.factor) %>% 
  dplyr::select(., "SiteCode", "TrapName", "Species", "N", "P", "C") %>% 
  filter(., SiteCode == "BL" & Species != "ABBA" & Species != "BEPA") %>% 
  droplevels() %>%
  pivot_longer(., cols = N:C, names_to = "Element", values_to ="Content") 

epPalette <- c("#f1b6da","#b8e186")

epPlot <- ggplot(data = epData, aes(x = Species, y = Content, fill = Species)) + 
  scale_fill_manual(values = epPalette) +
  scale_color_manual(values = epPalette) +
  geom_boxjitter(aes(fill = Species), jitter.shape = 21, outlier.shape = 21, 
                 outlier.intersect = TRUE, alpha = 0.75,
                 jitter.size = 3, outlier.size = 3) +
  ylab("Element Content (% dry weight)") +
  scale_x_discrete(labels = c("Red Maple", "Blueberry")) +
  facet_wrap(~Element, scales = "free_y")+
  theme_classic() +
  theme(legend.position = "none",
        text = element_text(size = 22))

ggsave(epPlot, filename = "../Results/epPlot.pdf", device = "pdf", dpi = 600, width = 12, height = 8)
```
 
## Browsing Data visualization

Here we present a simple bar plot of the frequency with which we recorded browsing
by snowshoe hare on our four plant species of interest. We collected browsing data 
during the summer of 2016, as we collected samples to describe and model the
elemental phenotype of each plant species. BLueberry and red maple are, overall,
the more browsed plants in our study area, followed by white birch. However, no
StDM ranked higher than the intercept for white birch, so we excluded it from
our analyses of home range size and plant stoichiometry.

```{r plant-browse, echo=TRUE, tidy=TRUE}
browseData <- read.csv("../Data/Plant_Browse.csv", header = TRUE) %>% dplyr::rename(., c(hareBrowse = porp._H_browse)) %>% dplyr::select(., -porp._M_browse)

# head(browseData)

browseData$hareBrowse <- as.factor(browseData$hareBrowse)

species_labeller <- c(
  "ABBA" = "Balsam Fir",
  "ACRU" = "Red Maple",
  "BEPA" = "White Birch",
  "VAAN" = "Blueberry"
)


ggplot(data = browseData, aes(x = hareBrowse)) + 
  geom_bar(aes(fill = Species, col = Species), alpha = 0.5) + 
  scale_x_discrete(labels = c("Not Browsed", "Browsed")) +
  scale_fill_ptol() +
  scale_color_ptol() +
  xlab("Hare Browsing") +
  ylab(" ") +
  facet_wrap(.~Species, ncol = 4, nrow = 1, 
             labeller = as_labeller(species_labeller),) + 
  theme_classic() +
  theme(legend.position = "none",
        text = element_text(size = 12))
```

## Relationship among Body Weight, Age, and Sex

Here we show the relationships between snowshoe hare body weight and age, and 
body weight and sex in our sample. Note that we could not build a true correlation
matrix or run a true correlation analysis due to the categorical nature of both 
age and sex. 

We use body weight as a proxy for age in our models due to the fairly strong 
differences between young and adult body weight. Conversely, while no clear 
body weight difference emerges between sexes, we exclude the variable sex from our
analyses due to the lack of clear evidence of a difference in the elemental 
phenotype between sexes snowshoe hares [@Rizzuto2019] and because of the overall
evidence of females being --- on average --- larger than males [@Feldhamer2003].
```{r hare-bw-age-sex, echo=TRUE, tidy=TRUE }
hare.rich$Age <- factor(hare.rich$Age, levels = c("Young", "Adult", "Unknown"))

age <- ggplot(data = hare.rich, aes(x = Age, y = WeightSSH_g)) + geom_boxplot() + ylab("Body Weight (g)") + theme_classic() + theme(panel.background = element_rect(fill = "transparent"), plot.background = element_rect(fill = "transparent", color = NA), axis.text = element_text(size = 16), axis.title = element_text(size = 20))

sex <- ggplot(data = hare.rich, aes(x = Sex, y = WeightSSH_g)) + geom_boxplot() + ylab("Body Weight (g)") + theme_classic() + theme(panel.background = element_rect(fill = "transparent"), plot.background = element_rect(fill = "transparent", color = NA), axis.text = element_text(size = 16), axis.title = element_text(size = 20))  

age + sex
```


## Stoichiometric Ratios values vs Individuals' Core Area Size {.tabset .tabset-fade .tabset-pills}

### C:N Ratio
```{r ACRU-HR-1, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(x = ACRU_CN_mean, y = HRsize, shape = SamplingYear)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Red Maple Mean C:N") + 
  ylab("Home Range Size (ha)") + 
  theme_classic()
```

```{r VAAN-HR-1, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(x = VAAN_CN_mean, y = HRsize, shape = SamplingYear)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) +
  xlab("Blueberry Mean C:N") + 
  ylab("Home Range Size (ha)") + 
  theme_classic()
```

### N:P Ratio
```{r ACRU-HR-2, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(x = ACRU_NP_mean, y = HRsize, shape = SamplingYear)) + geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + xlab("Red Maple Mean N:P") + ylab("Home Range Size (ha)") + theme_classic()
```

```{r VAAN-HR-2, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(x = VAAN_NP_mean, y = HRsize, shape = SamplingYear)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Blueberry Mean N:P") + 
  ylab("Home Range Size (ha)") + 
  theme_classic()
```

### C:P Ratio
```{r VAAN-HR-3, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(x = VAAN_CP_mean, y = HRsize, shape = SamplingYear)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Blueberry C:P") + 
  ylab("Home Range Size (ha)") + 
  theme_classic()
```

## Stoichiometric ratios mean vs CV {.tabset .tabset-fade .tabset-pills}

### Red Maple C:N
```{r acrucn-mean-vs-cvar, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(ACRU_CN_mean, y = ACRU_CN_CVar)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Average") + 
  ylab("Coefficient of Variation") + 
  theme_classic() 
```

### Red Maple N:P
```{r acrunp-mean-vs-cvar, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(ACRU_NP_mean, y = ACRU_NP_CVar)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Average") + 
  ylab("Coefficient of Variation") + 
  theme_classic() 
```

### Blueberry C:N
```{r vaancn-mean-vs-cvar, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(VAAN_CN_mean, y = VAAN_CN_CVar)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Average") + 
  ylab("Coefficient of Variation") + 
  theme_classic() 
```

### Blueberry N:P
```{r vaannp-mean-vs-cvar, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(VAAN_NP_mean, y = VAAN_NP_CVar)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) +
  xlab("Average") + 
  ylab("Coefficient of Variation") + 
  theme_classic() 
```

### Blueberry C:P
```{r vaancp-mean-vs-cvar, echo=TRUE, tidy=TRUE}
ggplot(hare.stoich, aes(VAAN_CP_mean, y = VAAN_CP_CVar)) + 
  geom_point(aes(fill = SamplingYear), shape = 21, size = 4, alpha = 0.5) + 
  xlab("Average") + 
  ylab("Coefficient of Variation") + 
  theme_classic() 
```

## Literature Review -- Elemental and Nutritional Content of Food

In our study, we use Nitrogen (N) as our main indicator of food quality --- 
alongside Phosphorus. However, not all N contained in a plant is available for 
consumers to be assimilated in their own biomass. Some of it may be locked in 
structural compounds that pass through the digestive tract of animals, and thus
it may get egested. As we do not have macromolecular data on the two fractions 
-- available and unavailable -- of N present in our plant SOIs, we turned to the 
literature. We collected data from studies included in two recent reviews 
[@Felton2018; @Champagne2020] of the influence different elements and 
macromolecular compounds have on diet selection of two groups of herbivores, 
Cervids and Leporids. 

We selected studies from the @Felton2018 and @Champagne2020 publicly available 
datasets based on whether they measured N in plant samples. We then collected 
data on their elemental, macromolecular, and phytochemical composition, by 
extracting it from tables and figures. This produced the dataset shown below.

```{r nvmn_dataload, echo=TRUE, tidy=TRUE}
stoichMNrev <- read.csv("../Data/StoichMN_Review.csv")

# set categorical variables as factors
stoichMNrev$ID <- as.factor(stoichMNrev$ID)
stoichMNrev$PhenUnits <- as.factor(stoichMNrev$PhenUnits)
stoichMNrev$StoichUnits <- as.factor(stoichMNrev$StoichUnits)
stoichMNrev$MnUnits <- as.factor(stoichMNrev$MnUnits)

kable(head(stoichMNrev)) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

We then further refined our dataset to include only those studies recording data
in either % dry matter/mass or % dry weight. 

```{r nvm_clean1, echo=TRUE, tidy=TRUE}
drymassRev <- filter(stoichMNrev, MnUnits == "% dry mass" | MnUnits == "% dry matter" | MnUnits == "% dry weight") 

kable(head(drymassRev)) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

Finally, as studies consistently reported only N or Protein content data -- since
the latter is routinely estimated using the 6.25 conversion factor 
[@Jones1931; @Mariotti2008] -- we subset the dry-mass-only dataset to include
only N-reporting studies.

```{r nvmn_clean2, echo = TRUE, tidy = TRUE}
onlyN <- drymassRev[complete.cases(drymassRev[, 7]),]
onlyN <- droplevels(onlyN)

kable(head(onlyN)) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

Now, we visually inspect the relationship between N content and the content of 
six C-based structural and non-structural macromolecules: Cellulose, 
Hemicellulose, Lignin, Neutral Detergent Fiber, Acid Detergent Fiber, and 
Total Non-Structural Carbohydrates. 

**Note:** The code below produces Figure S8 in the Supporting Information
document, hence we report here only the code to produce it. 

```{r nvmn_analyses, echo=TRUE, message=FALSE, warning=FALSE, tidy=TRUE, fig.show='hide'}
# create the formula object to use to print the OLS regression equation on the 
# plots using stat_poly_eq()
myformula <- y ~ x

# create palette for factors with large number of levels
colourCount = length(unique(onlyN$ID))
getPalette = colorRampPalette(brewer.pal(14, "Set3"))

# NDF
mn1 <- ggplot(onlyN, aes(x = N, y = NDF)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Neutral Detergent Fiber (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# ADF
mn2 <- ggplot(onlyN, aes(x = N, y = ADF)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Acid Detergent Fiber (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# Lignin
mn3 <- ggplot(onlyN, aes(x = N, y = Lignin)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Lignin (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# Carbohydrates
mn4 <- ggplot(onlyN, aes(x = N, y = Carbohydrate)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Total Non-Structural Carbohydrate (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# Cellulose
mn5 <- ggplot(onlyN, aes(x = N, y = Cellulose)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Cellulose (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# Hemicellulose
mn6 <- ggplot(onlyN, aes(x = N, y = Hemicellulose)) + 
  geom_smooth(method = "lm", colour = "black") + 
  geom_point(aes(fill = ID), shape = 21, size = 4) + 
  scale_fill_manual(values = getPalette(colourCount)) + 
  stat_poly_eq(formula = myformula, 
               aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")), 
               parse = TRUE, hjust = -.7) + 
  xlab("Nitrogen Content (% dry matter)") + 
  ylab("Hemicellulose (% dry matter)") + 
  theme_classic() + 
  theme(panel.grid.major.y = element_line(colour = "gray", linetype = "dotted"))

# Combine them all together
mn1 + mn2 + mn3 + mn4 +  mn5 + mn6 + plot_layout(ncol = 3, nrow = 2, 
                                                 guides = "collect") + 
  plot_annotation(tag_levels = "a", tag_prefix = "(", tag_suffix = ")")

# save it
ggsave("../Results/NvsMNuts.pdf", device = 'pdf', dpi = 600, width = 14, height = 8)
```

## Overlap vs stoich

We want to investigate if, in areas of high resource quality (i.e., low average  
stoichiometric ratios values) or low variability in resource quality (i.e., low 
coefficient of variation values), we have more or less overlap among snowshoe 
hare home ranges. Here, we calculate mean utilization distribution overlap 
using `overlap` in `ctmm`, then plot it against the home range's mean
stoichiometry and coefficient of variation (CV).

```{r overlap, echo=TRUE, tidy=TRUE, message=FALSE}
# calculate overlap
aKDEolap <- overlap(homeRanges, level = 0.95, debias = TRUE) 

# convert to dataframe of mean overlap
meanAKDEolap <- adply(aKDEolap, c(1,2)) %>%  # convert to dataframe
  dplyr::rename(., UD1=X1, UD2=X2) %>% # rename X1 and X2 to identify the UDs being compared
  dplyr::select(., UD1, UD2, est) %>% # retain only necessary columns
  dplyr::filter(., est != 1) %>% # remove overlap measure of self-to-self
  dplyr::group_by(., UD2, .add = TRUE) %>% # group by the right hand size of the comparison
  dplyr::summarise(., mean = mean(est), n = n()) %>% # get the mean overlap by group, i.e. collar frequency
  dplyr::rename(., CollarFrequency = UD2, meanBA = mean) %>% # rename variables once again
  dplyr::select(., -n) # drop unnecessary columns

# now, join with the hare.stoich dataframe
hare.stoich.olap <- inner_join(hare.stoich, meanAKDEolap)

# plots of mean overlap vs stoich
a1 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = ACRU_CN_mean)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Mean Red Maple C:N") + ggtitle("Red Maple C:N") + theme_classic()

a2 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = ACRU_NP_mean)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Mean Red Maple N:P") + ggtitle("Red Maple N:P") + theme_classic()

a3 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_CN_mean)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Mean Blueberry C:N") + ggtitle("Blueberry C:N") + theme_classic()

a4 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_NP_mean)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Mean Blueberry N:P") + ggtitle("Blueberry N:P") + theme_classic()

a5 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_CP_mean)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Mean Blueberry C:P") + ggtitle("Blueberry C:P") + theme_classic()

atot <- a1 + a2 + a3 + a4 + a5 + plot_annotation(title = "Mean Stoichiometry and Mean home range overlap (BA)") + plot_layout(guides = "collect")

atot

# plots of mean overlap vs stoich CV
b1 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = ACRU_CN_CVar)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Red Maple C:N CV") + ggtitle("Red Maple C:N") + theme_classic()

b2 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = ACRU_NP_CVar)) +  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Red Maple N:P CV") + ggtitle("Red Maple N:P") + theme_classic()

b3 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_CN_CVar)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Blueberry C:N CV") + ggtitle("Blueberry C:N") + theme_classic()

b4 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_NP_CVar)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1)  + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Blueberry N:P CV") + ggtitle("Blueberry N:P") + theme_classic()

b5 <- ggplot(hare.stoich.olap, aes(x = meanBA, y = VAAN_CP_CVar)) + geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) + geom_point(aes(color = CollarFrequency)) + xlab("Mean home range overlap (BA)") + ylab("Blueberry C:P CV") + ggtitle("Blueberry C:P") + theme_classic()

btot <- b1 + b2 + b3 + b4 + b5 + plot_annotation(title = "Stoichiometry CV and Mean home range overlap (BA)") + plot_layout(guides = "collect")

btot
```

## Kernel Utilization Distributions

Here we present kUD estimates for the home range of each of our snowshoe hares, 
drawing both the 50% ("core area"), 75%, and 90% isopleths on top of a 
heat map of the whole Utilization Distribution.

```{r akde-maps, echo=TRUE, tidy=TRUE, message=FALSE, warning=FALSE}

# setup hare points
hares.points <- hares.triangd %>% dplyr::select(., -COVt.x.y, -COV.x.x, -COV.y.y, -pid.x, -pid.y, -id.x, -id.y, -cpid) %>% dplyr:: rename(., CollarFrequency = indiv, Easting = long, Northing = lat)

# remove pseudoreplicated individuals
hares.points <- subset(hares.points, hares.points$CollarFrequency != "149.653" & 
                        hares.points$CollarFrequency != "149.053" & 
                        hares.points$CollarFrequency != "149.003" & 
                        hares.points$CollarFrequency != "149.274" &
                        hares.points$CollarFrequency != "149.555")

coordinates(hares.points) <- c("Easting", "Northing")
proj4string(hares.points) <- CRS("+init=epsg:4326")

# convert hare.points to sf
hares.points <- st_as_sf(hares.points)

# remove pseudoreplicated home ranges UDs
homeRangesClean <- homeRanges
names(homeRangesClean) <- names(homeRanges)
homeRangesClean <- homeRangesClean[-c(1,2,8,18)]

# extract the UD contours at 50%, 75%, and 90% isopleths
homeRanges.50 <- lapply(1:length(homeRangesClean), function(x) SpatialPolygonsDataFrame.UD(homeRangesClean[[x]], level.UD=0.50, level = 0.95))
homeRanges.75 <- lapply(1:length(homeRangesClean), function(x) SpatialPolygonsDataFrame.UD(homeRangesClean[[x]], level.UD=0.75, level = 0.95))
homeRanges.90 <- lapply(1:length(homeRangesClean), function(x) SpatialPolygonsDataFrame.UD(homeRangesClean[[x]], level.UD=0.90, level = 0.95))


# create a palette for these lines
aKDE.pal <- c("#ef3b2c", "#fb6a4a", "#fc9272")

# create index vector for loop 
loopCIDs <- names(homeRangesClean)


# allocate empty list to store maps
aKDE.maps <- list()

# loop to produce the maps

for (i in 1:length(loopCIDs)) {
  
  # add in ICR estimates
  aKDEpoly.50 <- homeRanges.50[[i]]
  aKDEpoly.75 <- homeRanges.75[[i]]
  aKDEpoly.90 <- homeRanges.90[[i]]
   
  # remove unnecessary polygons and rows
  aKDEpoly.50@polygons[c(1,3)] <- NULL
  aKDEpoly.50@data$name[c(1,3)] <- NA
  aKDEpoly.50@data <- drop_na(aKDEpoly.50@data)
  aKDEpoly.50@data$id <- "50%"
  
  aKDEpoly.75@polygons[c(1,3)] <- NULL
  aKDEpoly.75@data$name[c(1,3)] <- NA
  aKDEpoly.75@data <- drop_na(aKDEpoly.75@data)
  aKDEpoly.75@data$id <- "75%"
 
  aKDEpoly.90@polygons[c(1,3)] <- NULL
  aKDEpoly.90@data$name[c(1,3)] <- NA
  aKDEpoly.90@data <- drop_na(aKDEpoly.90@data)
  aKDEpoly.90@data$id <- "90%"

  # rbind ICR's estimates into a single SPDF
  aKDE.temp <- rbind(aKDEpoly.50, aKDEpoly.75, aKDEpoly.90)
  
  # convert ICR estimates to SpatialLinesDataFrame
  aKDE.lines.temp <- as(aKDE.temp, "SpatialLinesDataFrame")
  
  # convert ICR and MR home range contour lines to sf objects
  aKDEsf.temp <- st_as_sf(aKDE.lines.temp)
  
  # create a buonding box that update for each collar
  bbox_temp <- st_bbox(aKDEsf.temp) # current bounding box
  
  xrange <- bbox_temp$xmax - bbox_temp$xmin # range of x values
  yrange <- bbox_temp$ymax - bbox_temp$ymin # range of y values
  
  bbox_temp[1] <- bbox_temp[1] - (0.25 * xrange) # xmin - left
  bbox_temp[3] <- bbox_temp[3] + (0.25 * xrange) # xmax - right
  bbox_temp[2] <- bbox_temp[2] - (0.25 * yrange) # ymin - bottom
  bbox_temp[4] <- bbox_temp[4] + (0.25 * yrange) # ymax - top
  
  bbox_temp <- bbox_temp %>%  # take the bounding box ...
    st_as_sfc() # ... and make it a sf polygon
  
  # add in triangulation points
  points.temp <- dplyr::filter(hares.points, CollarFrequency == loopCIDs[i])
  
  # create a map using tmap and store it in its own slots in the list created
  # above
  aKDE.maps[[i]] <- 
    tm_shape(vaancnclip, bbox = bbox_temp, raster.downsample = FALSE) + 
    tm_raster(style = "pretty", palette = "-PRGn", 
              legend.show = TRUE, title = "Blueberry C:N", alpha = 0.5) + 
    tm_shape(bl_grid_pts) + 
    tm_dots(size = 0.3, shape = 18, col = "red", alpha = 0.3) + # grid trap locs
    tm_shape(points.temp) +
    tm_dots(size = 0.3, shape = 21, col = "blue", alpha = 0.3) +
    tm_shape(aKDEsf.temp) + 
    tm_lines(col = "id", palette = aKDE.pal, title.col = "% kUD -- ICR", lwd = 2) +
    tm_compass(position = c("right", "top")) +
    tm_scale_bar(width = 0.3, 
                 text.size = 1.25,
                 position = c("right", "bottom")) + 
    tm_layout(main.title = paste("Collar Frequency:", loopCIDs[i]),
              # title = paste("Ear tag:", dots.temp$EarTag),
              legend.outside = TRUE, 
              legend.outside.position = "right",
              legend.text.size = 1.1,
              legend.title.size = 1.25,
              asp = 1,
              frame = TRUE)

}

# arrange maps into a single visualization
aKDEmaps <- tmap_arrange(aKDE.maps)

aKDEmaps

tmap_save(aKDEmaps, filename = "../Results/aKDEmaps.pdf", width = 20, height = 20, dpi = 600)

rm(homeRangesClean)
```

## StDM Predictions Maps
Here we plot the predictions of ratios values for C:N, C:P, and N:P produced 
using Stoichiometric Distribution Models [@Leroux2017]. We used these 
predictions in the analyses above as estimates of the quality of plant food 
resources in the home ranges of our collared snowshoe hares. Note that here we
only present a map of the StDM predictions for blueberry C:N. If you would like
to see maps for blueberry C:P, N:P, and red maple C:N, N:P predictions, re-knit
this notebook after un-commenting the relevant lines of code in the chunk below.

```{r raster-Maps, echo=TRUE, warning=FALSE, tidy=TRUE, fig.cap="Map of our snowshoe hare live-trapping grid in the youngest forest stand (20-40 years old), with stoichiometric distribution models predictions for lowland blueberry C:N ratio."}

# Create a bounding box for the study area, to show in the inset reference map
st_bbox(bl_grid_pts)

bl.study.area <- st_bbox(bl_grid_pts) # current bounding box

xrange <- bl.study.area$xmax - bl.study.area$xmin # range of x values
yrange <- bl.study.area$ymax - bl.study.area$ymin # range of y values

bl.study.area[1] <- bl.study.area[1] - (0.75 * xrange) # xmin - left
bl.study.area[3] <- bl.study.area[3] + (0.75 * xrange) # xmax - right
bl.study.area[2] <- bl.study.area[2] - (0.75 * yrange) # ymin - bottom
bl.study.area[4] <- bl.study.area[4] + (0.75 * yrange) # ymax - top

bl.study.area <- bl.study.area %>%  # take the bounding box ...
  st_as_sfc() # ... and make it a sf polygon

# Mapping the raster underneath the grid and the 100% MCP
vaanCNmap <- tm_shape(vaancnclip, bbox = bl.study.area) + 
  tm_raster(style = "cont", palette = "-PRGn", 
            legend.show = TRUE, title = "Blueberry C:N", alpha = 0.75) + 
  # tm_shape(vaanCP, bbox = bl.study.area) + 
  # tm_raster(style = "cont", palette = "-PiYG", 
  #           legend.show = TRUE, title = "Blueberry C:P") + 
  # tm_shape(vaanNP, bbox = bl.study.area) + 
  # tm_raster(style = "cont", palette = "-BrBG", 
  #           legend.show = TRUE, title = "Blueberry N:P") + 
  # tm_shape(acruCN, bbox = bl.study.area) + 
  # tm_raster(style = "cont", palette = "-PRGn", 
  #           legend.show = TRUE, title = "Red Maple C:N") + 
  #  tm_shape(acruNP, bbox = bl.study.area) + 
  # tm_raster(style = "cont", palette = "-BrBG", 
  #           legend.show = TRUE, title = "Red Maple C:N") + 
  # tmap_options(max.raster = c(plot = 11308939, view = 11308939)) + 
  tm_shape(bl_grid_points) + tm_dots(size = 0.3, col = "red", shape = 18) + 
  # tm_shape(bl_all) + tm_polygons(alpha = 0, lty = 2, lwd = 5, 
  #                                border.col = "red") + 
  # tm_compass(position = c("right", "top")) + tm_scale_bar() + 
  tm_layout(legend.outside = TRUE, 
            legend.outside.position = "right")

# Mapping a reference map to include as an inset in the main map
# nl_map <- tm_shape(nlcoast)+ tm_polygons() + tm_shape(bl.study.area) + tm_polygons(col = "red", border.col = "red", lwd = 10)

# visualize
tmap_mode("plot")
vaanCNmap

# Save statement
# tmap_save(vaanCNmap, insets_tm = nl_map, insets_vp = viewport(x = .75, y = .166, width = 0.3, height = 0.3), height = 10, width = 18, filename = "../Results/BL_VaanCN.png", dpi = 300)
```

## Map of Study Area

```{r study-area-map-prep, echo=TRUE, tidy=TRUE}
# convert SiteName in the grid points shp file to a factor
grid_points_all$SiteName <- as.factor(grid_points_all$SiteName) 

# create color-blind safe palette
starea_palette <- c("#e28dbe", "#4d9221", "#4d9221", "#4d9221")

# Load a base map of the island of Newfoundland
nl_coastline <- read_sf(dsn = "../Data/Mapping/", layer = "NL_Dissolve1")

# load a base map of canada
canada <- read_sf(dsn = "../Data/Mapping/gpr_000b11a_e", layer = "gpr_000b11a_e")

# select only columns with names containing UTF-8 characters
canada <- canada[, c(1,3,5)]

# simplify the shapefile
canada_s <- ms_simplify(canada, keep = 0.001)

# make sure the shp file conforms to tmap requirements
canada_s <- st_make_valid(canada_s)

canada_s$PRUID <- as.factor(canada_s$PRUID)

# create coloring vectors for later
starea_col <- nrow(canada_s)
  
starea_col[c(2:13)] <- "white"
starea_col[1] <- "gray75"

# set crs for canada
canada_s <- st_transform(canada_s, st_crs(bl_grid_pts))


# Simplify the geometry of the coastline, simplifying the lines by removing 
# vertices, while preserving the topology
# This step should improve runtime of this section of the notebook
nlcoast<- ms_simplify(nl_coastline)

nlcoastsf <- st_as_sf(nlcoast, crs = st_crs(na_coastline))

nl_sf <- st_transform(nlcoastsf, crs = st_crs(bl_grid_pts))

# Create a bounding box for the study area, to show in the inset reference map
st_bbox(grid_points_all)

study.area <- st_bbox(c(xmin = 442963.0, xmax = 454538.4, 
                           ymin = 5358796.4, ymax = 5390664.8), 
                         crs = st_crs(grid_points_all)) %>% st_as_sfc()

study.area <- st_bbox(grid_points_all) # current bounding box

xrange <- study.area$xmax - study.area$xmin # range of x values
yrange <- study.area$ymax - study.area$ymin # range of y values

study.area[1] <- study.area[1] - (0.25 * xrange) # xmin - left
study.area[3] <- study.area[3] + (0.25 * xrange) # xmax - right
study.area[2] <- study.area[2] - (0.25 * yrange) # ymin - bottom
study.area[4] <- study.area[4] + (0.25 * yrange) # ymax - top

study.area <- study.area %>%  # take the bounding box ...
  st_as_sfc() # ... and make it a sf polygon

```

The interactive map below shows a snapshot of our study area, highlighted by the
red line, with the relative position of our live-trapping, meandering transect
shown by trap locations.

```{r study-area-map, echo=TRUE, tidy=TRUE}
# create the map of the study areas
starea_map_int <- tm_shape(study.area, is.master = T) + 
  tm_borders(col = "red", lwd = 5) + tm_shape(grid_points_all) +
  tm_symbols(col = "SiteName", size = 1, palette = starea_palette, border.col = "black") +
  tm_scale_bar(position = c("left", "bottom")) + 
  tm_basemap(server = "OpenTopoMap")

tmap_mode(mode = "view")
starea_map_int
```

Conversely, here we show the code to produce the static map of the study area
found in the Supplementary Information document. Note that we do not show the 
output of this code chunk, as it is already available in the SI.

```{r study-area-map-static, echo=TRUE, tidy=TRUE, message=FALSE}
tmap_mode("plot")
# create map of canada with newfoundland highlighted
canmap <- tm_shape(canada_s) + tm_polygons(col = "PRUID", palette = starea_col, alpha = 0.5) + tm_shape(study.area) + tm_symbols(col = "#e28dbe", border.col = "black", size = 0.5) + tm_layout(asp=1, inner.margins = c(0.01, 0.01, 0.01, 0.01), bg.color = NA, legend.show = F) 

# create the map of the study areas
starea_map <- tm_shape(nl_sf) + tm_borders() + tm_shape(grid_points_all) +
  tm_symbols(col = "SiteName", size = 1, palette = starea_palette, border.col = "black") + 
  tm_compass(position = c("right", "top"), size = 2, text.size = 2) + 
  tm_scale_bar(position = c("left", "bottom"), text.size = 1.2) +
  tm_layout(outer.margins = c(0.05, 0.01, 0.05, 0),
            inner.margins = c(0.02, 0.3, 0.02, 0),
            asp = 1.25,
            legend.show = F)

# starea_map
# 
# namap
# print(canmap, grid::viewport(x = 0.202, y = 0.73, width = 0.45, height = 0.45))

# save the map with inset
vp <- viewport(x = 0.227, y = 0.7332, width = 0.45, height = 0.45)

tmap_save(starea_map, insets_tm = canmap, insets_vp = vp, filename = "../Results/StudyAreaMap.pdf", dpi = 600)
```

