---
title: "Analyses of stoichiometry of larger home range estimates"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: "Matteo Rizzuto"
output:
  rmdformats::html_clean:
    self_contained: false
    thumbnails: true
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
    fig_width: 12
    fig_height: 8
    df_print: paged
  pdf_document:
    citation_package: biblatex
    dev: pdf
    fig_caption: true
    fig_width: 7
    fig_height: 2.64
    highlight: tango
    keep_tex: true
    latex_engine: pdflatex
    toc: true
    df_print: kable    
fontsize: 11pt
geometry: margin=1in
documentclass: article    
bibliography: ../Manuscripts/Rizzuto_etal_StoichHomeRanges.bib
csl: ../Manuscripts/functional-ecology.csl
editor_options: 
  chunk_output_type: inline
---

```{r eval=FALSE, include=FALSE, tidy=TRUE}
# if running as a standalone, change chunk options to evaluation this 
# code chunk
knitr::knit('HomeRangeEstimation.Rmd', tangle=TRUE)
source('HomeRangeEstimation.R')

knitr::knit('ModelStoichHR.Rmd', tangle=TRUE)
source('ModelStoichHR.R')

```

## Stoichiometry and Home Range Size --- 90% kUD
In this section, we investigate if the relationship between resource 
stoichiometry and home range size persist when using estimates of home range 
area produced from a larger kUD isopleth, e.g. 90%.

### Home range area at 90% kUD
First, we produce the necessary home range area estimates. Then, we use these 
to extract the resources stoichiometric data and extract summary statistics 
about them.
```{r 90-kud, echo=TRUE, tidy=TRUE}
# hrArea.90 <- kUD.hr.estimates[9, ]
# hrArea.90 <- tidyr::pivot_longer(hrArea.90, cols = 1:ncol(hrArea.90), names_to = "CollarFrequency", values_to = "HRsize", names_prefix = "X")
# 
# hares.kUDhr.90 <- getverticeshr(hares.kUD, percent = 90)
# 
# # allocate an empty list of projected kUD as Spatial objects
# stoich.hares.90 <- data.frame(CollarFrequency = character(0),
#                       # ABBA_CN = numeric(0), ABBA_CP = numeric(0), 
#                       ACRU_CN = numeric(0), ACRU_NP = numeric(0), 
#                       VAAN_CN = numeric(0), VAAN_CP = numeric(0), 
#                       VAAN_NP = numeric(0))
# 
# # remove collars with too few relocations for further analysis
# 
# hares.kUDhr.90$id <- as.factor(hares.kUDhr.90$id)
# 
# hares.kUDhr.90 <- subset(hares.kUDhr.90, 
#                          hares.kUDhr.90$id != "149.555" # &
#                          # hares.kUDhr.50$id != "150.032" &
#                          # hares.kUDhr.50$id != "150.052" &
#                          # hares.kUDhr.50$id != "150.154" 
#                          )
# 
# hares.kUDhr.90$id <- droplevels(hares.kUDhr.90$id)
# 
# # Create new indexing vector only for Bloomfield
# UniqCIDs.bl <- as.vector(droplevels(unique(hares.kUDhr.90$id)))
# 
# for (i in 1:length(UniqCIDs.bl)) {
#   # select the home range of interest
#   temp.hr.90 <- hares.kUDhr.90[hares.kUDhr.90$id == UniqCIDs.bl[i],]
#   
#   # transform CRS of temp.kUDhr to that of stoich_stack
#   temp.hr.90 <- spTransform(temp.hr.90, CRSobj = crs(stoich_stack))  
#   
#   # extract the stoich values for the home range of interest and store it 
#   # temporarily in a dataframe
#   temp.stoich.hr90 <- raster::extract(stoich_stack, 
#                                       temp.hr.90, method = "simple", 
#                                       weights = TRUE, df = TRUE, 
#                                       small = TRUE,
#                                       normalizeWeights = TRUE, 
#                                       cellnumbers = TRUE)
#   # browser()
#   
#   # assign home range id to the temporary stoich dataframe
#   temp.stoich.hr90$CollarFrequency <- UniqCIDs.bl[i]
#   
#   # bind the temporary stoich dataframe with the permanent one
#   
#   stoich.hares.90 <- dplyr::bind_rows(stoich.hares.90, temp.stoich.hr90)
#   
#   # projkUDsp.df <- na.omit(projkUDsp.df)
#   
#   # browser()
#   
#   # print(i)
# }

# And now let's store the summary stats in a dataset, potentially for future
# analysis
short.stoich.hares.90 <- stoich90 %>% group_by(CollarFrequency) %>% 
  summarise_at(.vars = vars(ACRU_CN, ACRU_NP, VAAN_CN, VAAN_CP, VAAN_NP), 
               .funs = list(~mean(., na.rm = TRUE), 
                            ~sd(., na.rm = TRUE), 
                            ~median(., na.rm = TRUE), 
                            ~min(., na.rm = TRUE), 
                            ~max(., na.rm = TRUE), 
                            ~mad(., na.rm = TRUE, low = TRUE), 
                            ~CVar(.)))

short.stoich.hares.90$CollarFrequency <- as.factor(short.stoich.hares.90$CollarFrequency)

kable(head(short.stoich.hares.90)) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

Now we merge the newly-produced dataframe containing the stoichiometry of resources at 90% kUD with the hare demographic data set.

```{r hr-models-pre-90, echo=TRUE, tidy=TRUE}
# make the kUD home range area SpatialPolygonsDataFrame into a "normal" dataframe
hares.HR90 <- hr_ninety[, c(1,3)] %>% 
  dplyr::rename(., CollarFrequency = frequency, HRsize = ninety)

# merge the demographic and kUD dataframes, then reorder the variables more 
# logically, and finalle break variable "Date" into its three components
# "Year", "Month", and "Day". "Year" will be important in later modelling. 
hareData90 <- merge(hareDemData, hares.HR90, 
                    by = "CollarFrequency") %>% 
  dplyr::select("CollarFrequency", "EarTag", "SiteName":"SamplingYear",
                "WeightSSH_g":"TickLoad", "HRsize", "DateTrapped", 
                "Comment") %>% 
  separate("DateTrapped", into = c("YearTrp", "MonthTrp", "DayTrp"), 
           sep = "-", remove = TRUE)

hareData90$SamplingYear <- as.factor(hareData90$SamplingYear)

# check for consistency in the collars present in the two datasets
# if the console returns <0 rows> all is good
dplyr::anti_join(hareData90, short.stoich.hares.90) 

# add the stoich data to the demographics-home range dataset
hare.stoich.90 <- merge(hareData90, short.stoich.hares.90, 
                        by = "CollarFrequency") %>% 
  dplyr::select("CollarFrequency", "EarTag", "SiteName", "Trap", "SamplingYear",
                "YearTrp":"DayTrp", "WeightSSH_g":"Sex", "HRsize", 
                "ACRU_CN_mean":"VAAN_NP_CVar")

kable(hare.stoich.90) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

<!-- Now, let's perform the random shuffling of the pseudoreplicated individuals, to  -->
<!-- ensure models only ever use 1 of the 2 home range estimates for the n = 4  -->
<!-- individuals that were followed for 2 years. -->

```{r pseudorep-randomsample-90, eval=FALSE, include=FALSE, tidy=TRUE}
# This code chunk randomly draws one out of each pair of pseudoreplicated entries
# in the hareData dataset (i.e., the entries with more than 1 year of sampling data)
hare.stoich.clean.90 <- do.call(rbind, lapply(split(hare.stoich.90, hare.stoich.90$EarTag), function(x) x[sample(nrow(x), 1), ]))

kable(hare.stoich.clean.90) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                fixed_thead = TRUE) %>% 
  scroll_box(width = "100%", height = "500px")
```

Again, the first test we perform is a test of the effect of sampling 
year on the size of snowshoe hare home range when estimated using the 75% kUD 
isopleth.

### Testing the Effect due to Sampling Year

#### Data-richness-based selection
An alternative element that may be influencing whether we have an effect of 
Sampling Year or not is the amount of telemetry data collected for a given 
individual in each sampling season. In the code chunk below, we fit a model of 
home range size as a function of sampling year using data only for the most 
data-rich year for the individuals that have two or more years of sampling.

```{r 90-year-models-3, echo=TRUE, tidy=TRUE}
hare.rich.90 <- subset(hare.stoich.90, hare.stoich.90$CollarFrequency != "149.653" & hare.stoich.90$CollarFrequency != "149.053" & hare.stoich.90$CollarFrequency != "149.003" & hare.stoich.90$CollarFrequency != "149.274")

hare.rich.mod <- lm(HRsize ~ SamplingYear, data = hare.rich.90) 

summary(hare.rich.mod)
lindia::gg_diagnose(hare.rich.mod)

ggplot(data = hare.rich.90, aes(x = SamplingYear, y = HRsize)) + geom_boxjitter(outlier.intersect = TRUE) + xlab("Sampling Year") + ylab("Home Range Size (ha)") + theme_classic() + theme(text = element_text(size = 18))
# ggsave(filename = "../Results/HRsizeDataRich.png")

# write.csv(hare.rich.90, file = "../Results/HareRichStoich_90kUD.csv")
```

#### Random draw of pseudoreplicates
Here, we randomly sample the four pairs of pseudoreplicated home range 
estimates 100 times and,for each of these 100 replicates, we run a simple 
linear model including only the Sampling Year as an explanatory variable.

```{r 90-years-model-1, echo=TRUE, tidy=TRUE}

hare.pseudo <- vector("list", length = 100)
year_mods <- vector("list", length = 100) 

for (i in 1:length(year_mods)) {

hare.pseudo[[i]] <- do.call(rbind, lapply(split(hare.stoich.90, hare.stoich.90$EarTag), function(x) x[sample(nrow(x), 1), ]))

year_mods[[i]] <- lm(HRsize ~ SamplingYear, data = hare.pseudo[[i]]) 

# gg_diagnose(year_mods[[i]])

# browser()
}

yearmods_kab <- purrr::map_dfr(year_mods, broom::tidy, .id = "model")

kable(yearmods_kab) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = TRUE) %>%
  pack_rows(index = table(fct_inorder(yearmods_kab$model))) %>%
  scroll_box(width = "100%", height = "500px")
```

#### Year-based selection
It is possible that the increasing temporal distance between the plant 
stoichiometric data collected in 2016 and the snowshoe hare telemetry data 
collected in 2017, 2018, and 2019 may be affecting the results of the models 
including only Sampling Year. To test for this, the code chunk below runs a 
model on a dataset of home range size estimate that include data based on when 
they were collected: for individuals with 2 or more years of data collection, 
we include only the home range size estimate obtained from the year closer to 
the plant sampling.

```{r 90-year-models-2, echo=TRUE, tidy=TRUE}
hare.year.90 <- subset(hare.stoich.90, hare.stoich.90$CollarFrequency != "150.173" & hare.stoich.90$CollarFrequency != "149.294" & hare.stoich.90$CollarFrequency != "149.003" & hare.stoich.90$CollarFrequency != "150.314")

hare.year.mod <- lm(HRsize ~ SamplingYear, data = hare.year.90) 

# summary(hare.year.mod)
lindia::gg_diagnose(hare.year.mod)

ggplot(data = hare.year.90, aes(x = SamplingYear, y = HRsize)) + geom_boxjitter(outlier.intersect = TRUE) + xlab("Sampling Year") + labs(y=expression("Home range size (ha)")) + theme_classic() + theme(text = element_text(size = 18))
# ggsave(filename = "../Results/HRsizeSYear.png")
```

As in other analyses, since sampling year does not appear to influence our
snowshoe hare population's sampling size, in the analyses below we will use the
years with more data points for the 4 individuals for which we have more than
one year of telemetry sampling.

### Red Maple C:N  {.tabset .tabset-fade .tabset-pills}

Click on each tab to see the summary and diagnostic plots for each model.

#### Intercept-only
```{r 90-ACRU-CN-null, echo=TRUE, tidy=TRUE}
# 3. Red Maple CN mean
acrucnnull.90 <- lm(HRsize ~ 1, data = hare.rich.90)

summary(acrucnnull.90)
```

#### Mean-only
```{r 90-ACRU-CN-only, echo=TRUE, tidy=TRUE, warning=FALSE}
# Red Maple CN mean
acruCNhr.90 <- lm(HRsize ~ ACRU_CN_mean, data = hare.rich.90)

# check model output
summary(acruCNhr.90)
```

*Diagnostic plots*
```{r 90-ACRU-CN-only-diag, echo=TRUE, tidy=TRUE}
# diagnostic plots using lindia package

gg_diagnose(acruCNhr.90, theme = theme_classic())
```

#### Coeff. Var.-only
```{r 90-ACRU-CN-cv-only, echo=TRUE, tidy=TRUE, warning=FALSE}
acruCNcvhr.90 <- lm(HRsize ~ ACRU_CN_CVar, data = hare.rich.90)

# check model output
summary(acruCNcvhr.90)
```

*Diagnostic plots*
```{r 90-ACRU-CN-cv-only-diag, echo=TRUE, tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(acruCNcvhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-acrucn-1, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(acruCNcvhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = ACRU_CN_CVar, y = HRsize)) +
  geom_segment(aes(xend = ACRU_CN_CVar, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Average Blueberry N:P") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few()
```

#### Mean + Weight
```{r 90-ACRU-CN-multi,echo=TRUE,tidy=TRUE}
# 1. Red Maple CN mean
acruCNhr.exp.90 <- lm(HRsize ~ ACRU_CN_mean + WeightSSH_g, data = hare.rich.90)

# check model output
summary(acruCNhr.exp.90)
```

*Diagnostic Plots*
```{r 90-ACRU-CN-multi-diag,echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(acruCNhr.exp.90, theme = theme_classic())
```

#### Coeff. Var. + Weight
```{r 90-ACRU-CN-multi-cv,echo=TRUE,tidy=TRUE}
acruCNcv.exp.90 <- lm(HRsize ~ ACRU_CN_CVar + WeightSSH_g, data = hare.rich.90)

# check model output
summary(acruCNcv.exp.90)

# confint(acruCNcv.exp.90)
```

*Diagnostic Plots*
```{r 90-ACRU-CN-multi-cv-diag,echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(acruCNcv.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-acrucn-2, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(acruCNcv.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `ACRU_CN_CVar` = "Red Maple C:N Coefficient of Variation",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_wrap(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names), strip.position = "bottom") + 
  theme_few() +
  theme(strip.placement = "outside")
```

#### Mean + Coeff. Var.
```{r 90-plus-stoich-acrucn-1, echo=TRUE, tidy=TRUE}
acrucn.plus.90 <- lm(HRsize ~ ACRU_CN_mean+ACRU_CN_CVar, data = hare.rich.90)

summary(acrucn.plus.90)

# confint(acrucn.plus.90)
```

*Diagnostic Plots*
```{r 90-p-acrucn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrucn.plus.90, theme = theme_classic())
```

#### Mean * Coeff. Var.
```{r 90-joint-stoich-acrucn-1, echo=TRUE, tidy=TRUE}
acrucn.joint.90 <- lm(HRsize ~ ACRU_CN_mean*ACRU_CN_CVar, data = hare.rich.90)

summary(acrucn.joint.90)
```

*Diagnostic Plots*
```{r 90-js-acrucn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrucn.joint.90, theme = theme_classic())
```

#### Mean + Coeff. Var. + Weight
```{r 90-stoich-weight-acrucn-1, echo=TRUE, tidy=TRUE}
acrucn.sw.90 <- lm(HRsize ~ ACRU_CN_mean+ACRU_CN_CVar+WeightSSH_g, data = hare.rich.90)

summary(acrucn.sw.90)
```

*Diagnostic Plots*
```{r 90-sw-acrucn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrucn.sw.90, theme = theme_classic())
```

#### Mean * Coeff. Var. + Weight
```{r 90-jsw-stoich-acrucn-2, echo=TRUE, tidy=TRUE}
acrucn.jsw.90 <- lm(HRsize ~ ACRU_CN_mean*ACRU_CN_CVar+WeightSSH_g, data = hare.rich.90)

summary(acrucn.jsw.90)
```

*Diagnostic Plots*
```{r 90-jsw-acrucn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrucn.jsw.90, theme = theme_classic())
```

#### AICc Table
```{r 90-acrucn-aicc-tab, echo=TRUE, tidy=TRUE}
mods.90 <- list()
mods.90[[1]] <- acruCNhr.90
mods.90[[2]] <- acruCNcvhr.90
mods.90[[3]] <- acruCNhr.exp.90
mods.90[[4]] <- acruCNcv.exp.90
mods.90[[5]] <- acrucn.plus.90
mods.90[[6]] <- acrucn.joint.90
mods.90[[7]] <- acrucn.sw.90
mods.90[[8]] <- acrucn.jsw.90
mods.90[[9]] <- acrucnnull.90

mods.names <- c("HRsize ~ Mean C:N", #1
  "HRsize ~ C:N CV", #2
  "HRsize ~ Mean C:N + Weight", #3
  "HRsize ~ C:N CV + Weight", #4
  "HRsize ~ Mean C:N + C:N CV", # 5
  "HRsize ~ Mean C:N * C:N CV", #6
  "HRsize ~ Mean C:N + C:N CV + Weight", #7
  "HRsize ~ Mean C:N * C:N CV + Weight", #8
  "Intercept" #9 
)

acruCN_aicctab.90 <- aictab(mods.90, modnames = mods.names, second.ord = T, sort = T)

# Allocate and populate a list of adjusted R square values following the same order as the best of model created up off
rsq.90 <- list()
for (i in 1:length(mods.90)) {
  rsq.90[[i]] <- summary(mods.90[[i]])$r.squared
}
# add names to the adjusted R square values list
names(rsq.90) <- mods.names
rsqdf.90 <- enframe(rsq.90, name = "Modnames", value = "Rsq") %>% unnest(cols = c("Modnames", "Rsq"))

rsqdf.90$Modnames <- as_factor(rsqdf.90$Modnames)

# save the now complete AIC table as new objec
acruCNaicRsq.90 <- acruCN_aicctab.90 %>% merge(., rsqdf.90) %>% arrange(., Delta_AICc)  

# Generate publication quality AIC table
gt(acruCNaicRsq.90) %>% fmt_number(columns = 3:9, decimals = 3) %>% tab_header("Model Selection for Red Maple C:N - 90% kUD") %>% cols_label(Modnames ="Models formula", K = "K", AICc = "AICc", Delta_AICc = html("&Delta;AICc"), ModelLik ="Model Likelihood", AICcWt = "AICc Weight", LL ="Log-Lik", Cum.Wt = "Cumulative Weight", Rsq = html("R<sup>2</sup>"))
```

### Blueberry C:N  {.tabset .tabset-fade .tabset-pills}

Click on each tab to see the summary and diagnostic plots for each model.

#### Intercept-only
```{r 90-VAAN-CN-null, echo=TRUE, tidy=TRUE}
# 2. Blueberry CN mean
vaancnnull.90 <- lm(HRsize ~ 1, data = hare.rich.90)

summary(vaancnnull.90)
```

#### Mean-only
```{r 90-VAAN-CN-only, echo=TRUE, tidy=TRUE}
# 2. Blueberry CN mean
vaanCNhr.90 <- lm(HRsize ~ VAAN_CN_mean, data = hare.rich.90)

summary(vaanCNhr.90)

```

*Diagnostic plots*
```{r 90-VAAN-CN-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package

gg_diagnose(vaanCNhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-vaancn-1, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(vaanCNhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = VAAN_CN_mean, y = HRsize)) +
  geom_segment(aes(xend = VAAN_CN_mean, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Average Blueberry C:N") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few() +
  theme(text = element_text(size = 20))
```

#### Coeff. Var.-only
```{r 90-VAAN-CN-cv-only, echo=TRUE, tidy=TRUE}
vaanCNcvhr.90 <- lm(HRsize ~ VAAN_CN_CVar, data = hare.rich.90)

summary(vaanCNcvhr.90)
```

*Diagnostic plots*
```{r 90-VAAN-CN-cv-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(vaanCNcvhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-vaancn-2, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(vaanCNcvhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = VAAN_CN_CVar, y = HRsize)) +
  geom_segment(aes(xend = VAAN_CN_CVar, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Blueberry C:N Coefficient of Variation") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few()+
  theme(text = element_text(size = 20))
```

#### Mean + Weight
```{r 90-VAAN-CN-multi,echo=TRUE,tidy=TRUE}
# 2. Blueberry CN mean
vaanCNhr.exp.90 <- lm(HRsize ~ VAAN_CN_mean + WeightSSH_g, data = hare.rich.90)

summary(vaanCNhr.exp.90)
```

*Diagnostic Plots*
```{r 90-VAAN-CN-multi-diag,echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(vaanCNhr.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-vaancn-3, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(vaanCNhr.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `VAAN_CN_mean` = "Average Blueberry N:P",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_wrap(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names), strip.position = "bottom") + 
  theme_few() +
  theme(strip.placement = "outside")
```

#### Coeff. Var. + Weight
```{r 90-VAAN-CN-multi-cv,echo=TRUE,tidy=TRUE}
vaanCNcv.exp.90 <- lm(HRsize ~ VAAN_CN_CVar + WeightSSH_g, data = hare.rich.90)

summary(vaanCNcv.exp.90)
```

*Diagnostic Plots*
```{r 90-VAAN-CN-multi-cv-diag,echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(vaanCNcv.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-vaancn-4, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(vaanCNcv.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `VAAN_CN_CVar` = "Blueberry C:N Coefficient of Variation",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_grid(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names)) + 
  theme_few()
```

#### Mean + Coeff. Var.
```{r 90-plus-stoich-vaancn-1, echo=TRUE, tidy=TRUE}
vaancn.plus.90 <- lm(HRsize ~ VAAN_CN_mean+VAAN_CN_CVar, data = hare.rich.90)

summary(vaancn.plus.90)

confint(vaancn.plus.90)
```

*Diagnostic Plots*
```{r 90-p-vaancn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancn.plus.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-vaancn-5, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(vaancn.plus.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `VAAN_CN_mean` = "Average Blueberry C:N",
  `VAAN_CN_CVar` = "Blueberry C:N Coefficient of Variation"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_wrap(~ Covariate, scales = "free_x", 
             labeller = as_labeller(covariates_names),
             strip.position = 'bottom') + 
  theme_few() +
  theme(strip.placement = "outside")
```

#### Mean * Coeff. Var.
```{r 90-joint-stoich-vaancn-1, echo=TRUE, tidy=TRUE}
vaancn.joint.90 <- lm(HRsize ~ VAAN_CN_mean*VAAN_CN_CVar, data = hare.rich.90)

summary(vaancn.joint.90)

confint(vaancn.joint.90)
```

*Diagnostic Plots*
```{r 90-js-vaancn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancn.joint.90, theme = theme_classic())
```

#### Mean + Coeff. Var. + Weight
```{r 90-stoich-weight-vaancn-1, echo=TRUE, tidy=TRUE}
vaancn.sw.90 <- lm(HRsize ~ VAAN_CN_mean+VAAN_CN_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaancn.sw.90)

confint(vaancn.sw.90)
```

*Diagnostic Plots*
```{r 90-sw-vaancn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancn.sw.90, theme = theme_classic())
```

#### Mean * Coeff. Var. + Weight
```{r 90-jsw-stoich-vaancn-2, echo=TRUE, tidy=TRUE}
vaancn.jsw.90 <- lm(HRsize ~ VAAN_CN_mean*VAAN_CN_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaancn.jsw.90)
```

*Diagnostic Plots*
```{r 90-jsw-vaancn-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancn.jsw.90, theme = theme_classic())
```

#### AICc Table
```{r 90-vaancn-aicc-tab, echo=TRUE, tidy=TRUE}
mods.90 <- list()
mods.90[[1]] <- vaanCNhr.90
mods.90[[2]] <- vaanCNcvhr.90
mods.90[[3]] <- vaanCNhr.exp.90
mods.90[[4]] <- vaanCNcv.exp.90
mods.90[[5]] <- vaancn.plus.90
mods.90[[6]] <- vaancn.joint.90
mods.90[[7]] <- vaancn.sw.90
mods.90[[8]] <- vaancn.jsw.90
mods.90[[9]] <- vaancnnull.90

mods.names <- c("HRsize ~ Mean C:N", #1
  "HRsize ~ C:N CV", #2
  "HRsize ~ Mean C:N + Weight", #3
  "HRsize ~ C:N CV + Weight", #4
  "HRsize ~ Mean C:N + C:N CV", # 5
  "HRsize ~ Mean C:N * C:N CV", #6
  "HRsize ~ Mean C:N + C:N CV + Weight", #7
  "HRsize ~ Mean C:N * C:N CV + Weight", #8
  "Intercept" #9 
)

vaanCN_aicctab.90 <- aictab(mods.90, modnames = mods.names, second.ord = T, sort = T)

# Allocate and populate a list of adjusted R square values following the same order as the best of model created up off
rsq.90 <- list()
for (i in 1:length(mods.90)) {
  rsq.90[[i]] <- summary(mods.90[[i]])$r.squared
}
# add names to the adjusted R square values list
names(rsq.90) <- mods.names
rsqdf.90 <- enframe(rsq.90, name = "Modnames", value = "Rsq") %>% unnest(cols = c("Modnames", "Rsq"))

rsqdf.90$Modnames <- as_factor(rsqdf.90$Modnames)

# save the now complete AIC table as new object
vaanCNaicRsq.90 <- vaanCN_aicctab.90 %>% merge(., rsqdf.90) %>% arrange(., Delta_AICc)  

# Generate publication quality AIC table
gt(vaanCNaicRsq.90) %>% fmt_number(columns = 3:9, decimals = 3) %>% tab_header("Model Selection for Blueberry C:N - 90% kUD") %>% cols_label(Modnames ="Models formula", K = "K", AICc = "AICc", Delta_AICc = html("&Delta;AICc"), ModelLik ="Model Likelihood", AICcWt = "AICc Weight", LL ="Log-Lik", Cum.Wt = "Cumulative Weight", Rsq = html("R<sup>2</sup>"))
```

### Red Maple N:P  {.tabset .tabset-fade .tabset-pills}

Click on each tab to see the summary and diagnostic plots for each model.

#### Intercept-only
```{r 90-ACRU-NP-null, echo=TRUE, tidy=TRUE}
# 3. Red Maple NP mean
acrunpnull.90 <- lm(HRsize ~ 1, data = hare.rich.90)

summary(acrunpnull.90)
```

#### Mean-only
```{r 90-ACRU-NP-only, echo=TRUE, tidy=TRUE}
# 3. Red Maple NP mean
acruNPhr.90 <- lm(HRsize ~ ACRU_NP_mean, data = hare.rich.90)

summary(acruNPhr.90)
```

*Diagnostic plots*
```{r 90-ACRU-NP-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package

gg_diagnose(acruNPhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-acrunp-1, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(acruNPhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = ACRU_NP_mean, y = HRsize)) +
  geom_segment(aes(xend = ACRU_NP_mean, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Average Red Maple N:P") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few() +
  theme(text = element_text(size = 20))
```

#### Coeff. Var.-only
```{r 90-ACRU-NP-cv-only, echo=TRUE, tidy=TRUE}
acruNPcvhr.90 <- lm(HRsize ~ ACRU_NP_CVar, data = hare.rich.90)

summary(acruNPcvhr.90)
```

*Diagnostic plots*
```{r 90-ACRU-NP-cv-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(acruNPcvhr.90, theme = theme_classic())
```

#### Mean + Weight
```{r 90-ACRU-NP-multi,echo=TRUE,tidy=TRUE}
# 3. Red Maple NP mean
acruNPhr.exp.90 <- lm(HRsize ~ ACRU_NP_mean + WeightSSH_g, data = hare.rich.90)

summary(acruNPhr.exp.90)
```

*Diagnostic Plots*
```{r 90-ACRU-NP-multi-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(acruNPhr.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-acrunp-2, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(acruNPhr.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `ACRU_NP_mean` = "Average Red Maple N:P",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_wrap(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names), strip.position = "bottom") + 
  theme_few() +
  theme(strip.placement = "outside")
```

#### Coeff. Var. + Weight
```{r 90-ACRU-NP-multi-cv,echo=TRUE,tidy=TRUE}
acruNPcv.exp.90 <- lm(HRsize ~ ACRU_NP_CVar + WeightSSH_g, data = hare.rich.90)

summary(acruNPcv.exp.90)
```

*Diagnostic Plots*
```{r 90-ACRU-NP-multi-cv-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(acruNPcv.exp.90, theme = theme_classic())
```

#### Mean + Coeff. Var.
```{r 90-plus-stoich-acrunp-1, echo=TRUE, tidy=TRUE}
acrunp.plus.90 <- lm(HRsize ~ ACRU_NP_mean+ACRU_NP_CVar, data = hare.rich.90)

summary(acrunp.plus.90)

# confint(acrunp.plus.90)
```

*Diagnostic Plots*
```{r 90-p-acrunp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrunp.plus.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-acrunp-3, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(acrunp.plus.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `ACRU_NP_mean` = "Average Red Maple N:P",
  `ACRU_NP_CVar` = "Red Maple N:P Coefficient of Variation"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_wrap(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names), strip.position = "bottom") + 
  theme_few() +
  theme(strip.placement = "outside")
```

#### Mean * Coeff. Var.
```{r 90-joint-stoich-acrunp-1, echo=TRUE, tidy=TRUE}
acrunp.joint.90 <- lm(HRsize ~ ACRU_NP_mean*ACRU_NP_CVar, data = hare.rich.90)

summary(acrunp.joint.90)

# confint(acrunp.joint.90)
```

*Diagnostic Plots*
```{r 90-js-acrunp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrunp.joint.90, theme = theme_classic())
```

#### Mean + Coeff. Var. + Weight
```{r 90-stoich-weight-acrunp-1, echo=TRUE, tidy=TRUE}
acrunp.sw.90 <- lm(HRsize ~ ACRU_NP_mean+ACRU_NP_CVar+WeightSSH_g, data = hare.rich.90)

summary(acrunp.sw.90)

# confint(acrunp.sw.90)
```

*Diagnostic Plots*
```{r 90-sw-acrunp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrunp.sw.90, theme = theme_classic())
```

#### Mean * Coeff. Var. + Weight
```{r 90-jsw-stoich-acrunp-2, echo=TRUE, tidy=TRUE}
acrunp.jsw.90 <- lm(HRsize ~ ACRU_NP_mean*ACRU_NP_CVar+WeightSSH_g, data = hare.rich.90)

summary(acrunp.jsw.90)
```

*Diagnostic Plots*
```{r 90-jsw-acrunp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(acrunp.jsw.90, theme = theme_classic())
```

#### AICc Table
```{r 90-acrunp-aicc-tab, echo=TRUE, tidy=TRUE}
mods.90 <- list()
mods.90[[1]] <- acruNPhr.90
mods.90[[2]] <- acruNPcvhr.90
mods.90[[3]] <- acruNPhr.exp.90
mods.90[[4]] <- acruNPcv.exp.90
mods.90[[5]] <- acrunp.plus.90
mods.90[[6]] <- acrunp.joint.90
mods.90[[7]] <- acrunp.sw.90
mods.90[[8]] <- acrunp.jsw.90
mods.90[[9]] <- acrunpnull.90

mods.names <- c("HRsize ~ Mean N:P", #1
  "HRsize ~ N:P CV", #2
  "HRsize ~ Mean N:P + Weight", #3
  "HRsize ~ N:P CV + Weight", #4
  "HRsize ~ Mean N:P + N:P CV", # 5
  "HRsize ~ Mean N:P * N:P CV", #6
  "HRsize ~ Mean N:P + N:P CV + Weight", #7
  "HRsize ~ Mean N:P * N:P CV + Weight", #8
  "Intercept" #9 
)

acruNP_aicctab.90 <- aictab(mods.90, modnames = mods.names, second.ord = T, sort = T)

# Allocate and populate a list of adjusted R square values following the same order as the best of model created up off
rsq.90 <- list()
for (i in 1:length(mods.90)) {
  rsq.90[[i]] <- summary(mods.90[[i]])$r.squared
}
# add names to the adjusted R square values list
names(rsq.90) <- mods.names
rsqdf.90 <- enframe(rsq.90, name = "Modnames", value = "Rsq") %>% unnest(cols = c("Modnames", "Rsq"))

rsqdf.90$Modnames <- as_factor(rsqdf.90$Modnames)

# save the now complete AIC table as new objec
acruNPaicRsq.90 <- acruNP_aicctab.90 %>% merge(., rsqdf.90) %>% arrange(., Delta_AICc)  

# Generate publication quality AIC table
gt(acruNPaicRsq.90) %>% fmt_number(columns = 3:9, decimals = 3) %>% tab_header("Model Selection for Red Maple N:P - 90% kUD") %>% cols_label(Modnames ="Models formula", K = "K", AICc = "AICc", Delta_AICc = html("&Delta;AICc"), ModelLik ="Model Likelihood", AICcWt = "AICc Weight", LL ="Log-Lik", Cum.Wt = "Cumulative Weight", Rsq = html("R<sup>2</sup>"))
```

### Blueberry N:P  {.tabset .tabset-fade .tabset-pills}

Click on each tab to see the summary and diagnostic plots for each model.

#### Intercept-only
```{r 90-VAAN-NP-null, echo=TRUE, tidy=TRUE}
# 4. Blueberry NP mean
vaannpnull.90 <- lm(HRsize ~ 1, data = hare.rich.90)

summary(vaannpnull.90)
```

#### Mean-only
```{r 90-VAAN-NP-only, echo=TRUE, tidy=TRUE}
# 4. Blueberry NP mean
vaanNPhr.90 <- lm(HRsize ~ VAAN_NP_mean, data = hare.rich.90)

summary(vaanNPhr.90)
```

*Diagnostic plots*
```{r 90-VAAN-NP-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package

gg_diagnose(vaanNPhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-vaannp-1, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(vaanNPhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = VAAN_NP_mean, y = HRsize)) +
  geom_segment(aes(xend = VAAN_NP_mean, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Average Blueberry N:P") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few()
```

#### Coeff. Var.-only
```{r 90-VAAN-NP-cv-only, echo=TRUE, tidy=TRUE}
vaanNPcvhr.90 <- lm(HRsize ~ VAAN_NP_CVar, data = hare.rich.90)

summary(vaanNPcvhr.90)
```

*Diagnostic plots*
```{r 90-VAAN-NP-cv-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(vaanNPcvhr.90, theme = theme_classic())
```

#### Mean + Weight
```{r 90-VAAN-NP-multi,echo=TRUE,tidy=TRUE}
vaanNPhr.exp.90 <- lm(HRsize ~ VAAN_NP_mean + WeightSSH_g, data = hare.rich.90)

summary(vaanNPhr.exp.90)

# confint(vaanNPhr.exp.90)
```
*Diagnostic Plots*
```{r 90-VAAN-NP-multi-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(vaanNPhr.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-vaannp-2, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(vaanNPhr.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `VAAN_NP_mean` = "Average Blueberry N:P",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_grid(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names)) + 
  theme_few()
```

#### Coeff. Var. + Weight
```{r 90-VAAN-NP-multi-cv,echo=TRUE,tidy=TRUE}
vaanNPcv.exp.90 <- lm(HRsize ~ VAAN_NP_CVar + WeightSSH_g, data = hare.rich.90)

summary(vaanNPcv.exp.90)
```

*Diagnostic Plots*
```{r 90-VAAN-NP-multi-cv-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(vaanNPcv.exp.90, theme = theme_classic())
```

#### Mean + Coeff. Var.
```{r 90-plus-stoich-vaannp-1, echo=TRUE, tidy=TRUE}
vaannp.plus.90 <- lm(HRsize ~ VAAN_NP_mean+VAAN_NP_CVar, data = hare.rich.90)

summary(vaannp.plus.90)

# confint(vaannp.plus.90)
```

*Diagnostic Plots*
```{r 90-p-vaannp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaannp.plus.90, theme = theme_classic())
```

#### Mean * Coeff. Var.
```{r 90-joint-stoich-vaannp-1, echo=TRUE, tidy=TRUE}
vaannp.joint.90 <- lm(HRsize ~ VAAN_NP_mean*VAAN_NP_CVar, data = hare.rich.90)

summary(vaannp.joint.90)
```

*Diagnostic Plots*
```{r 90-js-vaannp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaannp.joint.90, theme = theme_classic())
```

#### Mean + Coeff. Var. + Weight
```{r 90-stoich-weight-vaannp-1, echo=TRUE, tidy=TRUE}
vaannp.sw.90 <- lm(HRsize ~ VAAN_NP_mean+VAAN_NP_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaannp.sw.90)
```

*Diagnostic Plots*
```{r 90-sw-vaannp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaannp.sw.90, theme = theme_classic())
```

#### Mean * Coeff. Var. + Weight
```{r 90-jsw-stoich-vaannp-1, echo=TRUE, tidy=TRUE}
vaannp.jsw.90 <- lm(HRsize ~ VAAN_NP_mean*VAAN_NP_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaannp.jsw.90)
```

*Diagnostic Plots*
```{r 90-jsw-vaannp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaannp.jsw.90, theme = theme_classic())
```

#### AICc Table
```{r 90-vaannp-aicc-tab, echo=TRUE, tidy=TRUE}
mods.90 <- list()
mods.90[[1]] <- vaanNPhr.90
mods.90[[2]] <- vaanNPcvhr.90
mods.90[[3]] <- vaanNPhr.exp.90
mods.90[[4]] <- vaanNPcv.exp.90
mods.90[[5]] <- vaannp.plus.90
mods.90[[6]] <- vaannp.joint.90
mods.90[[7]] <- vaannp.sw.90
mods.90[[8]] <- vaannp.jsw.90
mods.90[[9]] <- vaannpnull.90


mods.names <- c("HRsize ~ Mean N:P", #1
  "HRsize ~ N:P CV", #2
  "HRsize ~ Mean N:P + Weight", #3
  "HRsize ~ N:P CV + Weight", #4
  "HRsize ~ Mean N:P + N:P CV", #5
  "HRsize ~ Mean N:P * N:P CV", #6
  "HRsize ~ Mean N:P + N:P CV + Weight", #7
  "HRsize ~ Mean N:P * N:P CV + Weight", #8
  "Intercept"
)

vaanNP_aicctab.90 <- aictab(mods.90, modnames = mods.names, second.ord = T, sort = T)

# Allocate and populate a list of adjusted R square values following the same order as the best of model created up off
rsq.90 <- list()
for (i in 1:length(mods.90)) {
  rsq.90[[i]] <- summary(mods.90[[i]])$r.squared
}
# add names to the adjusted R square values list
names(rsq.90) <- mods.names
rsqdf.90 <- enframe(rsq.90, name = "Modnames", value = "Rsq") %>% unnest(cols = c("Modnames", "Rsq"))

rsqdf.90$Modnames <- as_factor(rsqdf.90$Modnames)

# save now complete AICc table to a new object
vaanNPaicRsq.90 <- vaanNP_aicctab.90 %>% merge(., rsqdf.90) %>% arrange(., Delta_AICc) 

gt(vaanNPaicRsq.90) %>% fmt_number(columns = 3:9, decimals = 3) %>% tab_header("Model Selection for Blueberry N:P - 90% kUD") %>% cols_label(Modnames ="Models formula", K = "K", AICc = "AICc", Delta_AICc = html("&Delta;AICc"), ModelLik ="Model Likelihood", AICcWt = "AICc Weight", LL ="Log-Lik", Cum.Wt = "Cumulative Weight", Rsq = html("R<sup>2</sup>"))
```

### Blueberry C:P  {.tabset .tabset-fade .tabset-pills}

Click on each tab to see the summary and diagnostic plots for each model.

#### Intercept-only
```{r 90-VAAN-CP-null, echo=TRUE, tidy=TRUE}
# 5. Blueberry CP mean
vaancpnull.90 <- lm(HRsize ~ 1, data = hare.rich.90)

summary(vaancpnull.90)
```

#### Mean-only
```{r 90-VAAN-CP-only, echo=TRUE, tidy=TRUE}
# 5. Blueberry CP mean
vaanCPhr.90 <- lm(HRsize ~ VAAN_CP_mean, data = hare.rich.90)

summary(vaanCPhr.90)
```

*Diagnostic plots*
```{r 90-VAAN-CP-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package

gg_diagnose(vaanCPhr.90, theme = theme_classic())
```

*Data vs Predicted Plot*
```{r 90-data-vs-pred-vaancp-1, echo=TRUE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals
hare.predplot <- augment(vaanCPhr.90, se_fit = TRUE) %>% dplyr::select(-c(.se.fit, .hat:.std.resid)) 

ggplot(hare.predplot, aes(x = VAAN_CP_mean, y = HRsize)) +
  geom_segment(aes(xend = VAAN_CP_mean, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("Average Blueberry C:P") +
  ylab("Home Range size (ha)") +
  ggtitle("90% kUD") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  theme_few()
```

#### Coeff. Var.-only
```{r 90-VAAN-CP-cv-only, echo=TRUE, tidy=TRUE}
vaanCPcvhr.90 <- lm(HRsize ~ VAAN_CP_CVar, data = hare.rich.90)

summary(vaanCPcvhr.90)
```

*Diagnostic plots*
```{r 90-VAAN-CP-cv-only-diag, echo=TRUE,tidy=TRUE}
# diagnostic plots using lindia package
gg_diagnose(vaanCPcvhr.90, theme = theme_classic())
```

#### Mean + Weight
```{r 90-VAAN-CP-multi,echo=TRUE,tidy=TRUE}
vaanCPhr.exp.90 <- lm(HRsize ~ VAAN_CP_mean + WeightSSH_g, data = hare.rich.90)

summary(vaanCPhr.exp.90)

# confint(vaanCPhr.exp.90)
```

*Diagnostic Plots*
```{r 90-VAAN-CP-multi-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(vaanCPhr.exp.90, theme = theme_classic())
```

<!-- *Data vs Predicted Plot* -->
```{r 90-data-vs-pred-vaancp-2, eval=FALSE, include=FALSE, tidy=TRUE}
# code from https://drsimonj.svbtle.com/visualising-residuals

hare.predplot <- augment(vaanCPhr.exp.90, se_fit = TRUE) %>% 
  dplyr::select(-c(.se.fit, .hat:.std.resid)) %>% 
  gather(key ="Covariate", value = "Value", -HRsize, -.fitted, -.resid, -.sigma, -.cooksd)

covariates_names <- c(
  `VAAN_CP_mean` = "Average Blueberry C:P",
  `WeightSSH_g` = "Snowshoe hare body weight (g)"
)

ggplot(hare.predplot, aes(x = Value, y = HRsize)) +
  geom_segment(aes(xend = Value, yend = .fitted), alpha = .2) +
  geom_smooth(method = "lm", se = T, color = "lightgrey", alpha =.1) +
  geom_point(aes(fill = .resid, size = abs(.resid)), shape = 21) +
  geom_point(aes(y = .fitted), shape = 5) +
  xlab("") +
  ylab("Home Range size (ha)") +
  scale_fill_gradient2(low = "#8e0152", mid = "#f7f7f7", high = "#276419") +
  guides(fill = FALSE, size = FALSE) +
  facet_grid(~ Covariate, scales = "free_x", labeller = as_labeller(covariates_names)) + 
  theme_few()
```

#### Coeff. Var. + Weight
```{r 90-VAAN-CP-multi-cv,echo=TRUE,tidy=TRUE}
vaanCPcv.exp.90 <- lm(HRsize ~ VAAN_CP_CVar + WeightSSH_g, data = hare.rich.90)

summary(vaanCPcv.exp.90)
```

*Diagnostic Plots*
```{r 90-VAAN-CP-multi-cv-diag,echo=TRUE,tidy=TRUE}
gg_diagnose(vaanCPcv.exp.90, theme = theme_classic())
```


#### Mean + Coeff. Var.
```{r 90-plus-stoich-vaancp-1, echo=TRUE, tidy=TRUE}
vaancp.plus.90 <- lm(HRsize ~ VAAN_CP_mean+VAAN_CP_CVar, data = hare.rich.90)

summary(vaancp.plus.90)

# confint(vaancp.plus.90)
```

*Diagnostic Plots*
```{r 90-p-vaancp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancp.plus.90, theme = theme_classic())
```

#### Mean * Coeff. Var.
```{r 90-joint-stoich-vaancp-1, echo=TRUE, tidy=TRUE}
vaancp.joint.90 <- lm(HRsize ~ VAAN_CP_mean*VAAN_CP_CVar, data = hare.rich.90)

summary(vaancp.joint.90)
```

*Diagnostic Plots*
```{r 90-js-vaancp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancp.joint.90, theme = theme_classic())
```

#### Mean + Coeff. Var. + Weight
```{r 90-stoich-weight-vaancp-1, echo=TRUE, tidy=TRUE}
vaancp.sw.90 <- lm(HRsize ~ VAAN_CP_mean+VAAN_CP_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaancp.sw.90)
```

*Diagnostic Plots*
```{r 90-sw-vaancp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancp.sw.90, theme = theme_classic())
```

#### Mean * Coeff. Var. + Weight
```{r 90-jsw-stoich-vaancp-1, echo=TRUE, tidy=TRUE}
vaancp.jsw.90 <- lm(HRsize ~ VAAN_CP_mean*VAAN_CP_CVar+WeightSSH_g, data = hare.rich.90)

summary(vaancp.jsw.90)
```

*Diagnostic Plots*
```{r 90-jsw-vaancp-diag, echo=TRUE, tidy=TRUE}
gg_diagnose(vaancp.jsw.90, theme = theme_classic())
```

#### AICc Table
```{r 90-vaancp-aicc-tab, echo=TRUE, tidy=TRUE}
mods.90 <- list()
mods.90[[1]] <- vaanCPhr.90
mods.90[[2]] <- vaanCPcvhr.90
mods.90[[3]] <- vaanCPhr.exp.90
mods.90[[4]] <- vaanCPcv.exp.90
mods.90[[5]] <- vaancp.plus.90 
mods.90[[6]] <- vaancp.joint.90
mods.90[[7]] <- vaancp.sw.90
mods.90[[8]] <- vaancp.jsw.90
mods.90[[9]] <- vaancpnull.90
 
mods.names <- c("HRsize ~ Mean C:P", #1
  "HRsize ~ C:P CV", #2
  "HRsize ~ Mean C:P + Weight", #3
  "HRsize ~ C:P CV + Weight", #4
  "HRsize ~ Mean C:P + C:P CV", #5
  "HRsize ~ Mean C:P * C:P CV", #6
  "HRsize ~ Mean C:P + C:P CV + Weight", #7
  "HRsize ~ Mean C:P * C:P CV + Weight", #8
  "Intercept"
)

vaanCP_aicctab.90 <- aictab(mods.90, modnames = mods.names, second.ord = T, sort = T)

# Allocate and populate a list of adjusted R square values following the same order as the best of model created up off
rsq.90 <- list()
for (i in 1:length(mods.90)) {
  rsq.90[[i]] <- summary(mods.90[[i]])$r.squared
}

# add names to the adjusted R square values list
names(rsq.90) <- mods.names
rsqdf.90 <- enframe(rsq.90, name = "Modnames", value = "Rsq") %>% unnest(cols = c("Modnames", "Rsq"))

rsqdf.90$Modnames <- as_factor(rsqdf.90$Modnames)

# save now complete AICc table to a new object
vaanCPaicRsq.90 <- vaanCP_aicctab.90 %>% merge(., rsqdf.90) %>% arrange(., Delta_AICc) 

gt(vaanCPaicRsq.90) %>% fmt_number(columns = 3:9, decimals = 3) %>% tab_header("Model Selection for Blueberry C:P - 90% kUD") %>% cols_label(Modnames ="Models formula", K = "K", AICc = "AICc", Delta_AICc = html("&Delta;AICc"), ModelLik ="Model Likelihood", AICcWt = "AICc Weight", LL ="Log-Lik", Cum.Wt = "Cumulative Weight", Rsq = html("R<sup>2</sup>"))
```

### Table summary of AICc top models
```{r 90-aicc-top-models, echo=TRUE, tidy=TRUE, warning=FALSE}
top.mods.90 <- list()

# Blueberry C:N ratio top models
top.mods.90[[1]] <- vaanCNaicRsq.90[1,]
top.mods.90[[2]] <- vaanCNaicRsq.90[5,]
top.mods.90[[3]] <- vaanCNaicRsq.90[7,]
top.mods.90[[4]] <- vaanCNaicRsq.90[9,]

# Blueberry N:P ratio top models
top.mods.90[[5]] <- vaanNPaicRsq.90[1,]

# Blueberry C:P ratio top models
top.mods.90[[6]] <- vaanCPaicRsq.90[1,]

# Red maple N:P ratio top models
top.mods.90[[7]] <- acruNPaicRsq.90[1,]

# Red maple C:N ratio top models
top.mods.90[[8]] <- acruCNaicRsq.90[1,]

top.mods.90 %>% bind_rows() %>% gt() %>% 
  fmt_number(columns = 3:9, decimals = 3) %>% 
  tab_row_group(., group = "Blueberry C:N top models", rows = c(1:4)) %>% 
  tab_row_group(., group = "Blueberry N:P top models", rows = c(5)) %>% 
  tab_row_group(., group = "Bluberry C:P top models", rows = c(6)) %>% 
  tab_row_group(., group = "Red Maple N:P top models", rows = c(7)) %>% 
  tab_row_group(., group = "Red Maple C:N top models", rows = c(8)) %>% 
  cols_hide(columns = vars(AICc, ModelLik, AICcWt, Cum.Wt)) %>% 
  cols_label(Modnames = "Model", K = "K", Delta_AICc = html("&Delta;AICc"), 
             LL ="LL", Rsq = html("R<sup>2</sup>"))
```

The table below includes a breakdown of the uninformative parameters we removed, 
for each stoichiometric ratio-plant species pair. 

Model group               Uninformative Parameters
-------------------       --------------------------------
Blueberry C:N ratio       Body Weight, Mean-CV interaction
Blueberry N:P ratio       None
BLueberry C:P ratio       None
Red maple N:P ratio       None
Red maple C:N ratio       None