---
title: "Supporting Code"
subtitle: "Forage stoichiometry predicts the home range size of a small terrestrial herbivore"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
author: 
  - Matteo Rizzuto^[<a href="https://orcid.org/0000-0003-3065-9140">https://orcid.org/0000-0003-3065-9140</a>, Memorial University of Newfoundland, <a href="mrizzuto@.mun.ca">mrizzuto@mun.ca</a>]
  - Shawn J. Leroux^[<a href="https://orcid.org/0000-0001-9580-0294">https://orcid.org/0000-0001-9580-0294</a>, Memorial University of Newfoundland]
  - Eric Vander Wal^[<a href="https://orcid.org/0000-0002-8534-4317">https://orcid.org/0000-0002-8534-4317</a>, Memorial University of Newfoundland]
  - Isabella C. Richmond^[<a href="https://orcid.org/0000-0001-5079-8442">https://orcid.org/0000-0001-5079-8442</a>, Memorial University of Newfoundland]
  - Travis R. Heckford^[<a href="https://orcid.org/0000-0002-3993-6450">https://orcid.org/0000-0002-3993-6450</a>, Memorial University of Newfoundland]
  - Juliana Balluffi-Fry^[<a href="https://orcid.org/0000-0002-2365-1055">https://orcid.org/0000-0002-2365-1055</a>, Memorial University of Newfoundland]
  - Yolanda F. Wiersma^[<a href="https://orcid.org/0000-0003-4604-9240">https://orcid.org/0000-0003-4604-9240</a>, Memorial University of Newfoundland]
output:
  rmdformats::html_clean:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: true
    highlight: tango
    code_folding: hide
    fig_width: 12
    fig_height: 8
    df_print: paged
    toc_depth: 2
  pdf_document:
    citation_package: biblatex
    dev: pdf
    fig_caption: true
    fig_width: 7
    fig_height: 2.64
    highlight: tango
    keep_tex: true
    latex_engine: pdflatex
    toc: true
    df_print: kable    
fontsize: 11pt
geometry: margin=1in
documentclass: article    
bibliography: ../Manuscripts/Rizzuto_etal_StoichHomeRanges.bib
csl: ../Manuscripts/oikos.csl
editor_options: 
  chunk_output_type: inline
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex} 
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell}
  - \usepackage{xcolor} 
  - \usepackage{fontawesome5}  
---

# Introduction
This document details the workflow for our analyses investigating whether resource
elemental composition influences consumer home range size. We focus on a 
study system including the snowshoe hare (*Lepus americanus*) and two of its
preferred summer forage species, red maple (*Acer rubrum*) and lowland 
blueberry (*Vaccinium angustifolium*). The present document contains:

* code to estimate the location of each snowshoe hare from daily telemetry 
sessions in the field (May--September, 2016 to 2019)
* code to estimate home range size of 30 snowshoe hares using an autocorrelated
kernel density estimator (aKDE)
* code to extract C:N, C:P, and N:P ratios values from within snowshoe hare home 
ranges from StDM-predicted surfaces of spatial elemental composition of red 
maple and blueberry 
* code to run models investigating the relationship between resource 
stoichiometry and home range size, at three Utilization Distribution isopleths: 
50% (the "core area"), 75%, and 90%
* code to produce the figures in the main text and for visual supporting 
materials

You can use the interactive menu on the right to navigate between the different
sections of the document. 

## Naming conventions in this document
In the following, we make use acronyms for species' names, using different 
acronyms for the same species in the text, R code chunks, and 
dataframe column headers. In particular, in the text we routinely use the 
common name of a species, followed by either the full (on first use) or 
shortened latin name. In dataframes and code, we use an acronym derived from the 
first two letters of the genus name and the first two letters from the species 
name. The following table should be helpful in keeping track of what is what.

Latin name                  Common Name             Acronym
-----------------------     -----------             -------
*Acer rubrum*               Red maple               ACRU
*Vaccinium angustifolium*   Lowland blueberry       VAAN

## Recompiling this notebook

Running spatial analyses in R -- even not overly complicated
ones like those included in this document -- is a fairly computation-intensive 
endeavour. As such, if you plan to re-run the analyses reported here, be advised
that is may tame **some** time. Currently, recompiling this notebook can take
around **6-7 hours**, depending on your machine hardware configuration. We 
highlight each of the more time-consuming and computationally intensive 
code chunks and provide saved version of their outputs that can be loaded into 
your environment to speed up recompiling this notebook. Additionally, some of 
the objects produced during home range size estimation can be quite large, e.g. 
$\geq$ 2 Gb. 

As well, please note that this document uses relative paths and thus requires 
the following (or similar) folder structure for the code to run:

```
.
├── Code
├── Data
└── Results
```

In the above folder structure, the working directory to recompile this notebook 
should be set to **Code**.

Each section below is an individual, separate R notebook that can be found in 
the **Code** folder of this repository. The modular format of this document was 
inspired by: https://martinctc.github.io/blog/first-world-problems-very-long-rmarkdown-documents/


```{r include=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

## R packages used
This R notebook relies on several packages. Some of these are not available on 
CRAN, or are still in active development. These include packages 
`razimuth`, `gt`, and `SDMTools`. 

`razimuth` [@Gerber2018] allows for estimating the position of 
a transmitting collar from a set of three or more azimuthal bearings collected 
in the field through triangulation. `razimuth`is not on CRAN and is not 
maintained anymore. Crucially, however, `razimuth` allows to estimate error 
ellipses around radiocollar locations and these ellipses can be taken into
account to estimate home range size using package `ctmm` [@Fleming2017,@Fleming2019].
We load `razimuth` from the author's GitHub archive repository, 
where it is stored in its last stable version. 

`SDMTools` is a CRAN-archived package that provides a set of tools for 
processing the output of species distribution models. We will load it from the 
CRAN's GitHub repository.

`gt` is a package currently development that facilitates the production of 
information-rich data tables. We load it from the RStudio team own GitHub 
repository.

All of the other packages in use are available through CRAN. Package loading is 
done using the `easypackages` package, which makes it easy to seamlessly load 
and install packages from both within and outside the CRAN.

> **Please note** that, as of the time of this writing ---
`r format(Sys.Date(), "%B %Y")` --- big changes are underway for spatial 
analyses in R. The two foundational libraries used to run spatial analyses in 
R,`PROJ` and `GDAL`, are undergoing significant updates. As such, several 
thousand packages that enable users to perform spatial analyses in R and that 
rely on these two libraries are undergoing updates as well. In particular, for 
the code presented in this notebook, interested packages include `sf`, `sp`, and
`rgdal`.These packages need to be installed and/or upgraded from the same source
--- e.g. either binary (preferred) or from their respective development sources. 
Mixing installations can lead to the code below not working anymore or producing 
unexpected results. The analyses below work with this configuration of packages 
and dependencies:

```{r echo=TRUE, tidy=TRUE}
rgdal::rgdal_extSoftVersion()
```

> The code below is optimized to run using `GDAL` version 3.x and above, and 
`PROJ` version 6.x and above.

```{r pkg-file-load, echo=TRUE, tidy=TRUE, message=FALSE}
# Load packages that are either no longer maintained, not on CRAN, or in development
easypackages::packages("rstudio/gt", "cran/SDMTools", "cppek/razimuth" , "easypackages")

# Load all other packages required
packages("devtools", "plyr", "tidyverse", "rgdal", "rgeos", "sp", "maptools", 
         "tmap", "ctmm", "patchwork", "tmaptools", "adehabitatHR", "gdtools", 
         "ggmap", "ggrepel", "ggsci", "ggthemes", "maps", "spatial", "reshape2", 
         "dismo", "sf", "raster", "rasterVis", "nlme", "ggpol", "grid", "lme4", 
         "MuMIn", "lmerTest", "rmapshaper", "broom", "broom.mixed", 
         "kableExtra", "patchwork",  "AICcmodavg", "RColorBrewer", "sfheaders",
         "geosphere", "lindia", "formatR", "stringr", "data.table", "chron",
         "ggpmisc")
```


# Triangulation Observer Error 
<!-- The following code chunk loads the Rmd file in which we estimate the error
in triangulation associated with two of the observers that collected data in the 
field-->
```{r child=here::here("1_TriangulationError.Rmd")}

```

# Radiocollar Triangulation
<!-- The following code chunk loads the starting Rmd, which is the one where we 
estimate the location of collars in the field using razimuth. -->
```{r child=here::here("2_razimuthTriangulation.Rmd")}

```

# Home Range estimation and Stoichiometric Data extraction
<!-- The following code chunk loads the Rmd file to estimate home range size 
using ctmm and then extract data on foliage stoichiometry of plant species from
inside the home range-->
```{r child=here::here("3_aKDEHomeRangeEstimation.Rmd")}

```

# Home Range Overlap
<!-- The following code chunk loads the Rmd file in which we investigate the 
overlap in home range between consecutive years for four snowshoe hares -->
```{r child=here::here("4_HomeRangeOverlap.Rmd")}

```

# Modelling and Analyses
<!-- The following code chunk loads the model Rmd for our analyses at 50% kUD. -->
```{r child=here::here("5_ModelStoichHR.Rmd")}

```

<!-- This next code chunk repeats our analyses on the home range size of our snowshoe hares estimated using the 75% isopleth in the kUD. -->
```{r child=here::here("6_75kUDHRModels.Rmd")}

```

<!-- This next code chunk repeats our analyses on the home range size of our snowshoe hares estimated using the 90% isopleth in the kUD. -->
```{r child=here::here("7_90kUDHRModels.Rmd")}

```

# Visual Supporting Materials
<!-- Finally, this code chunk loads graphical supporting materials that allow for visualizing each hare's kernel Utilization Distribution, as well as the spatial distribution and variability of plant stoichiometry. -->
```{r child=here::here("8_AdditionalPlots.Rmd")}

```

# References